---
title: "Ch1_Wolf_modelDistribution"
author: "Erin Tattersall"
date: "May 8, 2018"
output: word_document
---

Modelling detections rates between November 2015 and April 2018 for wolves.  
Deciding on most appropriate distribution for response variable.


Proportion of zeros in data
```{r setup, message=FALSE, echo=FALSE}
knitr::opts_knit$set(root.dir = 'C:/Users/ETattersall/Desktop/Algar_Cam_Traps/Algar_Camera_Traps/Data') #Setting working directory for all code chunks
library(glmmTMB)
library(bbmle) #AICtab function
library(ggplot2)
library(lmtest)
library(reshape)
library(dplyr)
```
```{r, echo=FALSE, message=FALSE}
#Load detection data
det <- read.csv("Seismic_nov2015-apr2018.csv")
det$X <- NULL

#Load lowland data
low <- read.csv("newAVIE_lowland8buffersizes.csv")

#Combine data
det$low250 <- low$low250[match(det$Site, low$CamStation)]
det$low500 <- low$low500[match(det$Site, low$CamStation)]
det$low750 <- low$low750[match(det$Site, low$CamStation)]
det$low1000 <- low$low1000[match(det$Site, low$CamStation)]
det$low1250 <- low$low1250[match(det$Site, low$CamStation)]
det$low1500 <- low$low1500[match(det$Site, low$CamStation)]
det$low500 <- low$low500[match(det$Site, low$CamStation)]
det$low2000 <- low$low2000[match(det$Site, low$CamStation)]

#Load linedensity data
LineDens <- read.csv("AlgarStationsLD_Lines.csv")

# Combine datasets
det$LD250 <- LineDens$X250m[match(det$Site, LineDens$CamStation)]
det$LD500 <- LineDens$X500m[match(det$Site, LineDens$CamStation)]
det$LD750 <- LineDens$X750m[match(det$Site, LineDens$CamStation)]
det$LD1000 <- LineDens$X1000m[match(det$Site, LineDens$CamStation)]
det$LD1250 <- LineDens$X1250m[match(det$Site, LineDens$CamStation)]
det$LD1500 <- LineDens$X1500m[match(det$Site, LineDens$CamStation)]
det$LD1250 <- LineDens$X1750m[match(det$Site, LineDens$CamStation)]
det$LD2000 <- LineDens$X2000m[match(det$Site, LineDens$CamStation)]


#Load line width and veg height
sp <- read.csv("Spatial_covariates.csv")

det$VegHt <- sp$VegHt[match(det$Site, sp$Site)]
det$LineWidth <- sp$LineWidth[match(det$Site, sp$Site)]

## Still missing Snow days, Distance to water

```
```{r, echo=FALSE, results='hide'}

#### Wolf models ####
## Lowland measured at 500m, LD measured at 1250m
# Not including Dist2Water --> no corresponding hypothesis

### Exploring distribution and overdispersion (code from Zuur & Ieno, 2016)
##1. Proportion of 0's in data
table(is.na(det$Wolf)) #1800 non-NAs --> no NAs present
table(det$Wolf == 0)
```
```{r}
sum(det$Wolf==0, na.rm = TRUE)/nrow(det)
```
  91% of the data is zeroes --> very likely zero-inflated.  

### Fitting a basic poisson GLM and checking overdispersion, using global model (doesn't yet include SnowDays)
```{r}
glm1 <- glmmTMB(Wolf~ Treatment + LineWidth + LD1250 + VegHt + low500 + ActiveDays, data = det, family = poisson)
# Residuals and overdispersion
E1 <- resid(glm1, type="pearson")
N <- nrow(det)
p <- length(coef(glm1))
sum(E1^2)/(N-p)
```
Dispersion value of  2.30 indicates overdispersion

Simulating data to check probability of calculated dispersion, given a Poisson GLM.
```{r, include=FALSE, echo=FALSE, warning=FALSE}
#function for calculating overdispersion (as above)
MyDispersion <- function(y, mu, N, p){
  e <- (y-mu)/sqrt(mu)
  sum(e^2)/(N-p)
}
muFit <- fitted(glm1) #fitted values from model
Ysim <- matrix(nrow = N, ncol = 10000) #matrix storing simulated responses
DispersionSim <- vector(length = 10000)#vector storing Dispersion value
#Loop running simulation of Poisson distributed data and calculating Dispersion value
for(i in 1:10000){
  Ysim[,i] <- rpois(N,lambda = muFit)
  DispersionSim[i] <- MyDispersion(Ysim[,i], muFit, N, p)
}
```
```{r, echo=FALSE}
#Histogram of dispersion statistics
hist(DispersionSim, xlim = c(0,3))# Simulated statistics are mostly on either side of 1
```
Histogram indicates that an overdispersion statistic of 2.30 is outside the likely distribution of dispersion statistics for Poisson distributed response variables, suggesting that Wolf data is likely overdispersed.  

Comparing the proportion of zeros in data to simulated zeros from model shows that Wolf data has more zeroes than would be expected in a Poisson GLM
```{r, echo=FALSE}
## Comparing proportions of 0's in simulated data to that in sampled data
zeros <- vector(length = 10000)
for(i in 1:10000){
  zeros[i] <- sum(Ysim[,i] == 0) / N
}

{plot(table(zeros),
     axes = FALSE,
     xlim = c(0.8,1),
     xlab = "Percentage of zeros",
     ylab = "Frequency")

axis(2)
axis(1, 
     at = c(0.82,0.84,0.86,0.88,0.90,0.92,0.94,0.96,0.98,1.0),
     labels = c("82%","84%","86%","88%","90%","92%","94%","96%","98%","100%"))
points(x = sum(det$Wolf==0, na.rm = TRUE)/ N,
       y = 0, pch = 16, cex = 5, col = 2)}
```
  This presents a case for using zero-inflated models, which can be verified with model selection of GLMMs
## Model selection: choosing model form and distribution  

Comparing the same GLMM (including random effects of Site and Month) modeled as a poisson, nb, ZIP and ZINB (with nbinom1 and nbinom2 differing in how variance changes with mean) yields:
```{r, message=FALSE}
## Model comparisons of distributions and zero-inflation
glm1 <- glmmTMB(Wolf~ Treatment + LineWidth + LD1250 + VegHt + low500 + ActiveDays + (1| Site) + (1|Month), data = det, family = poisson)
glm2 <- glmmTMB(Wolf~ Treatment + LineWidth + LD1250 + VegHt + low500 + ActiveDays + (1| Site) + (1|Month), data = det, family = nbinom1(link= "log")) #Warning 'matrix not positive definite'
glm3 <- glmmTMB(Wolf~ Treatment + LineWidth + LD1250 + VegHt + low500 + ActiveDays + (1| Site) + (1|Month), data = det, family = nbinom2(link = "log"))
glm4 <- glmmTMB(Wolf~ Treatment + LineWidth + LD1250 + VegHt + low500 + ActiveDays + (1| Site) + (1|Month), zi = ~1, data = det, family = poisson)
glm5 <- glmmTMB(Wolf~ Treatment + LineWidth + LD1250 + VegHt + low500 + ActiveDays +(1| Site) + (1|Month), zi = ~1, data = det, family = nbinom1(link= "log")) #Warning 'matrix not positive definite'
glm6 <- glmmTMB(Wolf~ Treatment + LineWidth + LD1250 + VegHt + low500 + ActiveDays + (1| Site) + (1|Month), zi = ~1, data = det, family = nbinom2(link= "log"))
```
```{r, echo=FALSE}
modnames <- c("Poisson", "Nbinom1", "Nbinom2", "ZIP", "ZINB1", "ZINB2")
ICtab(glm1,glm2,glm3,glm4,glm5,glm6, mnames = modnames, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)

```
Nbinom1 models showed warnings (see above), but output includes parameter estimates, so models are included. However, Nbinom2 distributions perform better
```{r, echo = FALSE}
summary(glm3)
```
 ZINB model output:
```{r, echo = FALSE}
summary(glm6)
```
 Active Days affects the probability of observing a zero in data --> should be included in ZI model. It could be argued that it should NOT be included in conditional. I will test both
```{r, warning=FALSE}
glm7 <- glmmTMB(Wolf~ Treatment + LineWidth + LD1250 + VegHt + low500 + ActiveDays +(1| Site) + (1|Month), zi = ~ActiveDays, data = det, family = nbinom2(link= "log"))
glm8 <- glmmTMB(Wolf~ Treatment + LineWidth + LD1250 + VegHt + low500 +(1| Site) + (1|Month), zi = ~ActiveDays, data = det, family = nbinom2(link= "log"))
```
```{r, echo=FALSE}
modnames <- c("Poisson", "Nbinom1", "Nbinom2", "ZIP", "ZINB1", "ZINB2", "ZINB2-AD1")
ICtab(glm1,glm2,glm3,glm4,glm5,glm6, glm8, mnames = modnames, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
summary(glm8)
```
 Model with ActiveDays in Conditional and ZI produced estimates, but not std. errors. Excluded.
 Including ActiveDays in the ZI model results in more logLikelihood of model and more AIC weight.
 For Wolf models, I will therefore use zero inflated GLMMs with a nbinom2 distribution (where variance changes quadratically with the mean), including ActiveDays in the ZI model.  
 # Model hypotheses  
 ## Finding random structure
```{r, echo=FALSE, message=FALSE}
r0 <- glmmTMB(Wolf~ LineWidth + LD1250 + VegHt + low500*Treatment, data = det, zi=~ActiveDays, family = nbinom2)
rSite <- glmmTMB(Wolf~ LineWidth + LD1250 + VegHt + low500*Treatment + (1|Site), data = det,zi=~ActiveDays, family = nbinom2) 
rMonth <- glmmTMB(Wolf~ LineWidth + LD1250 + VegHt + low500*Treatment + (1|Month), data = det,zi=~ActiveDays, family = nbinom2)
r2 <- glmmTMB(Wolf~ LineWidth + LD1250 + VegHt + low500*Treatment + (1|Site) + (1|Month), data = det, zi=~ActiveDays,family = nbinom2)
ICtab(r0, rSite, rMonth, r2, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
```
Continue modelling with 2 random effects
 