---
title: "Ch1_models_WTDeer"
author: "Erin Tattersall"
date: "May 11, 2018"
output: word_document
---

  Based on model selection comparison of underlying distributions and zero-inflation, I chose an nbinom1 distribution for WTDeer data, with zero-inflation and ActiveDays in the ZI model (see Ch1_WTDeer_modelDistribution.Rmd)    
Here I will: 
1. Double check random structure using all covariates
2. Build models assessing Treatment effect, including other combinations of covariates to account for additional noise and compare their effect to Treatment 
4. Perform model selection with AIC  
5. Calculate evidence ratios (AICwt of Best Model/ AICwt of other models)  
6. Checking residuals of Top Model
  
Previous scale analysis showed lowland habitat at 2000m and linear density measured at 750m best explained WTDeer detections


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(glmmTMB)
library(bbmle) #AICtab function
library(ggplot2)
library(lmtest)
library(reshape)
library(dplyr)
library(knitr)
library(MuMIn) #streamlining model selection

```
```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#Load detection data
det <- read.csv("Seismic_nov2015-apr2018.csv")

#Load lowland data
low <- read.csv("newAVIE_lowland8buffersizes.csv")

#Combine data
det$low250 <- low$low250[match(det$Site, low$CamStation)]
det$low500 <- low$low500[match(det$Site, low$CamStation)]
det$low750 <- low$low750[match(det$Site, low$CamStation)]
det$low1000 <- low$low1000[match(det$Site, low$CamStation)]
det$low1250 <- low$low1250[match(det$Site, low$CamStation)]
det$low1500 <- low$low1500[match(det$Site, low$CamStation)]
det$low1750 <- low$low1750[match(det$Site, low$CamStation)]
det$low2000 <- low$low2000[match(det$Site, low$CamStation)]

#Load linedensity data
LineDens <- read.csv("AlgarStationsLD_Lines.csv")

# Combine datasets
det$LD250 <- LineDens$X250m[match(det$Site, LineDens$CamStation)]
det$LD500 <- LineDens$X500m[match(det$Site, LineDens$CamStation)]
det$LD750 <- LineDens$X750m[match(det$Site, LineDens$CamStation)]
det$LD1000 <- LineDens$X1000m[match(det$Site, LineDens$CamStation)]
det$LD1250 <- LineDens$X1250m[match(det$Site, LineDens$CamStation)]
det$LD1500 <- LineDens$X1500m[match(det$Site, LineDens$CamStation)]
det$LD1750 <- LineDens$X1750m[match(det$Site, LineDens$CamStation)]
det$LD2000 <- LineDens$X2000m[match(det$Site, LineDens$CamStation)]


#Load line width and veg height
sp <- read.csv("Spatial_covariates.csv")

det$VegHt <- sp$VegHt[match(det$Site, sp$Site)]
det$LineWidth <- sp$LineWidth[match(det$Site, sp$Site)]


### Centring and standardizing covariates
## All continuous input variables need to be centred and standardized ((value - mean)/2SD; Gelman, 2008)
covscale <- function(covariate){
  centre <- (covariate - mean(covariate, na.rm = TRUE)) # where covariate is a vector of numeric input values for one covariate
  standardize <- centre/(2*sd(covariate, na.rm = TRUE)) # Divide centred value by 2 SD
}

summary(det$ActiveDays) #mean 18
sd(det$ActiveDays)
det$ActiveDays_sc <- covscale(det$ActiveDays)
summary(det$ActiveDays_sc)
sd(det$ActiveDays_sc)
det$D2W_sc <- covscale(det$Dist2Water_km) #mean 2.07
summary(det$Dist2Water_km) #mean 2.07
sd(det$Dist2Water_km) #1.76
summary(det$D2W_sc) #mean 0
sd(det$D2W_sc) #SD

det$pSnow_sc <- covscale(det$pSnow)
summary(det$pSnow_sc) #NAs, probably because of NAs in pSnow --> added na.rm = TRUE to function
det$pSnow_sc <- covscale(det$pSnow)
summary(det$pSnow_sc)
sd(det$pSnow_sc, na.rm = TRUE)
det$low250_sc <- covscale(det$low250)
det$low500_sc <- covscale(det$low500)
det$low750_sc <- covscale(det$low750)
det$low1000_sc <- covscale(det$low1000)
det$low1250_sc <- covscale(det$low1250)
det$low1500_sc <- covscale(det$low1500)
det$low1750_sc <- covscale(det$low1750)
det$low2000_sc <- covscale(det$low2000)
det$LD250_sc <- covscale(det$LD250)
det$LD500_sc <- covscale(det$LD500)
det$LD750_sc <- covscale(det$LD750)
det$LD1000_sc <- covscale(det$LD1000)
det$LD1250_sc <- covscale(det$LD1250)
det$LD1500_sc <- covscale(det$LD1500)
det$LD1750_sc <- covscale(det$LD1750)
det$LD2000_sc <- covscale(det$LD2000)
det$LineWidth_sc <- covscale(det$LineWidth)
det$VegHt_sc <- covscale(det$VegHt)

summary(det[ , 36:56]) #Centred means of 0

```
### 1. Random structure and Active Days 
  Random structure was previously assessed, but here I will confirm using all model covariates. Also comparing random intercepts vs random slope, and whether ActiveDays should be included in the conditional model.  

```{r, echo=FALSE, message=FALSE}
r0 <- glmmTMB(WTDeer~ LineWidth_sc + LD750_sc + VegHt_sc + low2000_sc + Treatment + pSnow_sc, data = det, zi=~ActiveDays_sc,family = nbinom1)
rSite <- glmmTMB(WTDeer~ LineWidth_sc + LD750_sc + VegHt_sc + low2000_sc + Treatment + pSnow_sc + (1|Site), data = det, zi=~ActiveDays_sc,  family = nbinom1) 
rMonth <- glmmTMB(WTDeer~ LineWidth_sc + LD750_sc + VegHt_sc + low2000_sc + Treatment + pSnow_sc + (1|Month), data = det, zi=~ActiveDays_sc, family = nbinom1)
r2 <- glmmTMB(WTDeer~ LineWidth_sc + LD750_sc + VegHt_sc + low2000_sc + Treatment + pSnow_sc + (1|Site) + (1|Month), data = det, zi=~ActiveDays_sc, family = nbinom1)
r2AD <- glmmTMB(WTDeer~ LineWidth_sc + LD750_sc + VegHt_sc + low2000_sc + Treatment + pSnow_sc + ActiveDays_sc + (1|Site) + (1|Month), data = det, zi=~ActiveDays_sc, family = nbinom1)
rSiteS <- glmmTMB(WTDeer~ LineWidth_sc + LD750_sc + VegHt_sc + low2000_sc + Treatment + pSnow_sc + (Treatment|Site), data = det,zi=~ActiveDays_sc, family = nbinom1) 
rMonthS <- glmmTMB(WTDeer~ LineWidth_sc + LD750_sc + VegHt_sc + low2000_sc + Treatment + pSnow_sc +  (Treatment|Month), data = det, zi=~ActiveDays_sc, family = nbinom1)
r2S <- glmmTMB(WTDeer~ LineWidth_sc + LD750_sc + VegHt_sc + low2000_sc + Treatment + pSnow_sc + (Treatment|Site) + (Treatment|Month), data = det, zi=~ActiveDays_sc, family = nbinom1)
ICtab(r0, rSite, rMonth, r2, r2AD, rSiteS, rMonthS, r2S, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
```  
  Random slope models fail to converge, so exclude. Continue modelling with 2 random effects. ActiveDays in conditional model had slightly less model weight, so continue modelling ActiveDays in ZI only.
## Model Set  (note that numbered models from dredge do not correspond with numbers in table; I have listed models in order of increasing complexity, dredge did not)

Model Name  | Covariates
----------- | -------------------
L0          | 1
L1          | Treatment
L2          | Treatment + low2000
L3          | Treatment + pSnow
L4          | Treatment + LineWidth 
L5          | Treatment + VegHt
L6          | Treatment + LD750
L7          | Treatment + low2000 + pSnow
L8          | Treatment + low2000 + LineWidth
L9          | Treatment + low2000 + VegHt
L10         | Treatment + low2000 + LD750
L11         | Treatment + pSnow + LineWidth
L12         | Treatment + pSnow + VegHt
L13         | Treatment + pSnow + LD750
L14         | Treatment + LineWidth + VegHt
L15         | Treatment + LineWidth + LD750
L16         | Treatment + VegHt + LD750
L17         | Treatment + low2000 + pSnow + LineWidth
L18         | Treatment + low2000 + pSnow + VegHt
L19         | Treatment + low2000 + pSnow + LD750
L20         | Treatment + low2000 + LineWidth + VegHt
L21         | Treatment + low2000 + LineWidth + LD750
L22         | Treatment + low2000 + VegHt + LD750
L23         | Treatment + pSnow + LineWidth + VegHt
L24         | Treatment + pSnow + LineWidth + LD750
L24         | Treatment + pSnow + VegHt + LD750
L25         | Treatment + LineWidth + VegHt + LD750
L26         | Treatment + low2000 + pSnow + LineWidth + VegHt
L27         | Treatment + low2000 + pSnow + LineWidth + LD750
L28         | Treatment + pSnow + LineWidth + VegHt + LD750
L29         | Treatment + low2000 + LineWidth + vegHt + LD750
L30         | Treatment + low2000 + pSnow + VegHt + LD750
L31         | Treatment + low2000 + pSnow + LineWidth + VegHt + LD750

```{r, echo=FALSE}
# dredge function from MuMin generatesand evaluates model sets
global.model <- glmmTMB(WTDeer~ LineWidth_sc + LD750_sc + VegHt_sc + low2000_sc + Treatment + pSnow_sc + (1|Site) + (1|Month), data = det, zi=~ActiveDays_sc, family = nbinom1)

#List of all possible models including Treatment and some combination of other covariates. Runs models and returns a model selection data frame
Treat.models <- dredge(global.model = global.model, beta = "none", evaluate = FALSE, rank = "AIC", fixed = ~cond(Treatment) + zi(ActiveDays_sc), trace = TRUE) # Does not include null model
#Lists model objects
Models <- get.models(Treat.models, subset = TRUE)

## Add NULL model to list
NULLmod <- glmmTMB(WTDeer~ (1|Site) + (1|Month), data = det, zi=~ActiveDays_sc, family = nbinom1)
Models[["Nullmod"]] <- NULLmod
glimpse(Models)
names(Models)

WTDeerAIC <- ICtab(Models, mnames = names(Models), type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
WTDeerAIC
``` 
```{r, echo=FALSE, results='hide'}
summary(Models$`30`)

## Compare estimates to those in model with unstandardized covariates
unstd.mod <- glmmTMB(WTDeer~ LD750 + low2000 + pSnow + VegHt + Treatment + (1|Site) + (1|Month), data = det, zi=~ActiveDays_sc, family = nbinom1)
summary(unstd.mod) ### Treatment coefficients are the same but continuous covariate coefficients are not. Significance is same
```
  Four models within 2 dAIC points of each other, with model weights between 14 - 34%.
    
  
## Evidence Ratios and Cumulative model weight (calculating confidence intervals)
  
  Calculating evidence ratios (AIC wt of best model/AIC weight of others) gives:
  
```{r,echo=FALSE, results='hide'}
EvR <- function(AICwt.high, AICwt.low){
  EvR <- AICwt.high/AICwt.low
  print(EvR)
}
EvR(WTDeerAIC$weight[1], WTDeerAIC$weight[2])
WTDeerWt <- WTDeerAIC$weight
WTDeerER <- vector(length=32)
for(i in 2:33){
  WTDeerER[i-1] <- EvR(WTDeerWt[1], WTDeerWt[i])
}
```
```{r,echo=FALSE}
WTDeerER <- append("", WTDeerER)
ER <- as.data.frame(names(Models))
colnames(ER) <- "ModelNames"
ER$dLogLikelihood <- WTDeerAIC$dLogLik
ER$dAIC <- WTDeerAIC$dAIC
ER$Modelweight <- WTDeerAIC$weight
ER$CumulativeWeight <- rep(NA,33)
ER$CumulativeWeight[1] <- ER$Modelweight[1]
for (i in 2:length(ER$Modelweight)){
  ER$CumulativeWeight[i] <- ER$Modelweight[i] + ER$CumulativeWeight[i-1]
}
ER$EvidenceRatio <- WTDeerER

ER
summary(Models$`32`)
```


### Plotting residuals against fitted values and predicted values for all covariates
```{r, echo=FALSE}

## Residual plot for global model(L12)
op <- par(mfrow = c(1,2))
pred <- predict(L12, zitype = "response")
resid <- residuals(L12)

## Plot residuals against predicted --> diagonal lines characteristic of discrete data

{plot(pred, resid, main = "Residuals vs. Predicted", xlab = "Predicted Values", ylab = "Residuals")
abline(h = 0, lty = 2)  
lines(smooth.spline(pred, resid))}
{plot(fitted(L12), residuals(L12), main= "Residuals vs Fitted", xlab = "Fitted Values", ylab = "Residuals")
abline(h = 0, lty = 2)
lines(smooth.spline(fitted(L12), resid))}



```
