---
title: "Ch1_models_Wolf"
author: "Erin Tattersall"
date: "May 11, 2018"
output: word_document
---

  Based on model selection comparison of underlying distributions and zero-inflation, I chose an nbinom1 distribution for Wolf data, with zero-inflation.
  I previously had decided to include ActiveDays in the ZI model. However, to retain the same amount of data in each model, I need to omit rows with NAs. NA rows are usually those in which cameras were inactive. Therefore, in the final dataset used in modelling, ActiveDays should have a greater effect on the count data, not the zero mass, so it should be included in the conditional model.
Here I will: 
1. Double check random structure using all covariates
2. Build models assessing Treatment effect, including other combinations of covariates to account for additional noise and compare their effect to Treatment 
4. Perform model selection with AIC  
5. Calculate evidence ratios (AICwt of Best Model/ AICwt of other models)  
6. Checking residuals of Top Model
  
Previous scale analysis showed lowland habitat at 500m and linear density measured at 1250m best explained Wolf detections


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(glmmTMB)
library(bbmle) #AICtab function
library(ggplot2)
library(lmtest)
library(reshape)
library(dplyr)
library(knitr)
library(MuMIn) #streamlining model selection

```
```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#Load detection data
det <- read.csv("Seismic_nov2015-2018.csv")

#Load lowland data
low <- read.csv("newAVIE_lowland8buffersizes.csv")

#Combine data
det$low250 <- low$low250[match(det$Site, low$CamStation)]
det$low500 <- low$low500[match(det$Site, low$CamStation)]
det$low750 <- low$low750[match(det$Site, low$CamStation)]
det$low1000 <- low$low1000[match(det$Site, low$CamStation)]
det$low1250 <- low$low1250[match(det$Site, low$CamStation)]
det$low1500 <- low$low1500[match(det$Site, low$CamStation)]
det$low1750 <- low$low1750[match(det$Site, low$CamStation)]
det$low2000 <- low$low2000[match(det$Site, low$CamStation)]

#Load linedensity data
LineDens <- read.csv("AlgarStationsLD_Lines.csv")

# Combine datasets
det$LD250 <- LineDens$X250m[match(det$Site, LineDens$CamStation)]
det$LD500 <- LineDens$X500m[match(det$Site, LineDens$CamStation)]
det$LD750 <- LineDens$X750m[match(det$Site, LineDens$CamStation)]
det$LD1000 <- LineDens$X1000m[match(det$Site, LineDens$CamStation)]
det$LD1250 <- LineDens$X1250m[match(det$Site, LineDens$CamStation)]
det$LD1500 <- LineDens$X1500m[match(det$Site, LineDens$CamStation)]
det$LD1750 <- LineDens$X1750m[match(det$Site, LineDens$CamStation)]
det$LD2000 <- LineDens$X2000m[match(det$Site, LineDens$CamStation)]


#Load line width and veg height
sp <- read.csv("Spatial_covariates.csv")

det$VegHt <- sp$VegHt[match(det$Site, sp$Site)]
det$LineWidth <- sp$LineWidth[match(det$Site, sp$Site)]


### Centring and standardizing covariates
## All continuous input variables need to be centred and standardized ((value - mean)/2SD; Gelman, 2008)
covscale <- function(covariate){
  centre <- (covariate - mean(covariate, na.rm = TRUE)) # where covariate is a vector of numeric input values for one covariate
  standardize <- centre/(2*sd(covariate, na.rm = TRUE)) # Divide centred value by 2 SD
}

summary(det$ActiveDays) #mean 18
sd(det$ActiveDays)
det$ActiveDays_sc <- covscale(det$ActiveDays)
summary(det$ActiveDays_sc)
sd(det$ActiveDays_sc)
det$D2W_sc <- covscale(det$Dist2Water_km) #mean 2.07
summary(det$Dist2Water_km) #mean 2.07
sd(det$Dist2Water_km) #1.76
summary(det$D2W_sc) #mean 0
sd(det$D2W_sc) #SD

det$pSnow_sc <- covscale(det$pSnow)
summary(det$pSnow_sc) #NAs, probably because of NAs in pSnow --> added na.rm = TRUE to function
det$pSnow_sc <- covscale(det$pSnow)
summary(det$pSnow_sc)
sd(det$pSnow_sc, na.rm = TRUE)
det$low250_sc <- covscale(det$low250)
det$low500_sc <- covscale(det$low500)
det$low750_sc <- covscale(det$low750)
det$low1000_sc <- covscale(det$low1000)
det$low1250_sc <- covscale(det$low1250)
det$low1500_sc <- covscale(det$low1500)
det$low1750_sc <- covscale(det$low1750)
det$low2000_sc <- covscale(det$low2000)
det$LD250_sc <- covscale(det$LD250)
det$LD500_sc <- covscale(det$LD500)
det$LD750_sc <- covscale(det$LD750)
det$LD1000_sc <- covscale(det$LD1000)
det$LD1250_sc <- covscale(det$LD1250)
det$LD1500_sc <- covscale(det$LD1500)
det$LD1750_sc <- covscale(det$LD1750)
det$LD2000_sc <- covscale(det$LD2000)
det$LineWidth_sc <- covscale(det$LineWidth)
det$VegHt_sc <- covscale(det$VegHt)



summary(det[ , 36:56]) #Centred means of 0

write.csv(det, "Seismic_nov2015-2018.csv")

#Omit NA rows
det <- na.omit(det)

```
### 1. Random structure and Active Days 
  Random structure was previously assessed, but here I will confirm using all model covariates. 

```{r, echo=FALSE, message=FALSE}
r0 <- glmmTMB(Wolf~ LineWidth_sc + LD1250_sc + VegHt_sc + low500_sc + Treatment + pSnow_sc + ActiveDays_sc, data = det, zi=~1,family = nbinom2)
rSite <- glmmTMB(Wolf~ LineWidth_sc + LD1250_sc + VegHt_sc + low500_sc + Treatment + pSnow_sc + ActiveDays_sc + (1|Site), data = det, zi=~1,  family = nbinom2) 
rMonth <- glmmTMB(Wolf~ LineWidth_sc + LD1250_sc + VegHt_sc + low500_sc + Treatment + pSnow_sc + ActiveDays_sc + (1|Month), data = det, zi=~1, family = nbinom2)
r2 <- glmmTMB(Wolf~ LineWidth_sc + LD1250_sc + VegHt_sc + low500_sc + Treatment + pSnow_sc + ActiveDays_sc + (1|Site) + (1|Month), data = det, zi=~1, family = nbinom2)
rSiteS <- glmmTMB(Wolf~ LineWidth_sc + LD1250_sc + VegHt_sc + low500_sc + Treatment + pSnow_sc + ActiveDays_sc + (Treatment|Site), data = det,zi=~1, family = nbinom2) 
rMonthS <- glmmTMB(Wolf~ LineWidth_sc + LD1250_sc + VegHt_sc + low500_sc + Treatment + pSnow_sc + ActiveDays_sc + (Treatment|Month), data = det, zi=~1, family = nbinom2)
r2S <- glmmTMB(Wolf~ LineWidth_sc + LD1250_sc + VegHt_sc + low500_sc + Treatment + pSnow_sc + ActiveDays_sc + (Treatment|Site) + (Treatment|Month), data = det, zi=~1, family = nbinom2)
ICtab(r0, rSite, rMonth, r2, rSiteS, rMonthS, r2S, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
```  
  Random slope models fail to converge, so exclude. Continue modelling with 2 random effects. 
## Model Set  
  (note that numbered models from dredge do not correspond with numbers in table; I have listed models in order of increasing complexity, dredge did not)
  Also: ActiveDays is also fixed in all models (including NULL)

Model Name  | Covariates
----------- | -------------------
L0          | 1
L1          | Treatment
L2          | Treatment + low500
L3          | Treatment + pSnow
L4          | Treatment + LineWidth 
L5          | Treatment + VegHt
L6          | Treatment + LD1250
L7          | Treatment + low500 + pSnow
L8          | Treatment + low500 + LineWidth
L9          | Treatment + low500 + VegHt
L10         | Treatment + low500 + LD1250
L11         | Treatment + pSnow + LineWidth
L12         | Treatment + pSnow + VegHt
L13         | Treatment + pSnow + LD1250
L14         | Treatment + LineWidth + VegHt
L15         | Treatment + LineWidth + LD1250
L16         | Treatment + VegHt + LD1250
L17         | Treatment + low500 + pSnow + LineWidth
L18         | Treatment + low500 + pSnow + VegHt
L19         | Treatment + low500 + pSnow + LD1250
L20         | Treatment + low500 + LineWidth + VegHt
L21         | Treatment + low500 + LineWidth + LD1250
L22         | Treatment + low500 + VegHt + LD1250
L23         | Treatment + pSnow + LineWidth + VegHt
L24         | Treatment + pSnow + LineWidth + LD1250
L24         | Treatment + pSnow + VegHt + LD1250
L25         | Treatment + LineWidth + VegHt + LD1250
L26         | Treatment + low500 + pSnow + LineWidth + VegHt
L27         | Treatment + low500 + pSnow + LineWidth + LD1250
L28         | Treatment + pSnow + LineWidth + VegHt + LD1250
L29         | Treatment + low500 + LineWidth + vegHt + LD1250
L30         | Treatment + low500 + pSnow + VegHt + LD1250
L31         | Treatment + low500 + pSnow + LineWidth + VegHt + LD1250

```{r, echo=FALSE, message=FALSE, results = 'hide'}
# dredge function from MuMin generates and evaluates model sets
global.model <- glmmTMB(Wolf~ Treatment + low500_sc + pSnow_sc + LineWidth_sc + LD1250_sc + VegHt_sc +  ActiveDays_sc + (1|Site) + (1|Month), data = det, zi=~1, family = nbinom2)

#List of all possible models including Treatment and some combination of other covariates. Runs models and returns a model selection data frame
Treat.models <- dredge(global.model = global.model, beta = "none", evaluate = TRUE, rank = "AIC", fixed = ~cond(Treatment) + cond(ActiveDays_sc), trace = TRUE) # Does not include null model

#Lists model objects
Models <- get.models(Treat.models, subset = TRUE)

## Add NULL model to list
NULLmod <- glmmTMB(Wolf~ ActiveDays_sc + (1|Site) + (1|Month), data = det, zi=~1, family = nbinom2)
Models[["Nullmod"]] <- NULLmod
names(Models)
```

```{r, echo=FALSE}
WolfAIC <- ICtab(Models, mnames = names(Models), type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
WolfAIC
``` 
```{r, echo=FALSE, results='hide'}
summary(Models$`13`)
summary(Models$`9`)
summary(Models$`14`)
summary(Models$`29`)
summary(Models$`15`)

```
  Five models within 2 dAIC points of each other, with model weights between 7 - 21%.
    
  
## Evidence Ratios and Cumulative model weight (calculating confidence intervals)
  
  Calculating evidence ratios (AIC wt of best model/AIC weight of others) gives:
  
```{r,echo=FALSE, results='hide'}
EvR <- function(AICwt.high, AICwt.low){
  EvR <- AICwt.high/AICwt.low
  print(EvR)
}
EvR(WolfAIC$weight[1], WolfAIC$weight[2])
WolfWt <- WolfAIC$weight
WolfER <- vector(length=32)
for(i in 2:33){
  WolfER[i-1] <- EvR(WolfWt[1], WolfWt[i])
}
```
```{r,echo=FALSE}
WolfER <- append("", WolfER)
ER <- as.data.frame(names(Models))
colnames(ER) <- "ModelNames"
ER$dLogLikelihood <- WolfAIC$dLogLik
ER$dAIC <- WolfAIC$dAIC
ER$Modelweight <- WolfAIC$weight
ER$CumulativeWeight <- rep(NA,33)
ER$CumulativeWeight[1] <- ER$Modelweight[1]
for (i in 2:length(ER$Modelweight)){
  ER$CumulativeWeight[i] <- ER$Modelweight[i] + ER$CumulativeWeight[i-1]
}
ER$EvidenceRatio <- WolfER

ER
```
 Examining summaries for top 8 models (2dAIC)  
```{r, echo=FALSE, results='hide'}
fixef(Models$`13`)
fixef(Models$`9`)
fixef(Models$`14`)
fixef(Models$`29`)
fixef(Models$`15`)

```  
Aside from Treatment and ActiveDays, all 5 models contain pSnow. 4 contain low, 1 each contains LineWidth, VegHt, or LD

### Pretending variables (NOT DONE FOR 36 MONTH DATA)
  Comparing deviance of top models - if covariate does not add much, resdiual deviance will be similar across models
  
 Model                                       | Est. + SE of possible pretending variables   | Residual Deviance
---------------------------------------------|----------------------------------------------|---------------------
Treat + pSnow + low + ActiveDays             |                                              | 1190.8
Treat + pSnow + low + LD + ActiveDays        |     LD 0.324 +/- 0.357                       | 1190.0
Treat + pSnow + ActiveDays                   |                                              | 1194.2
Treat + low + pSnow + LineWidth + ActiveDays |     LineWidth 0.164 +/- 0.380                | 1190.6
Treat + pSnow + low + VegHt + ActiveDays     |     VegHt 0.244 +/- 0.399                    | 1190.5


### Summary for full model
```{r, echo=FALSE}
## Summary for full model
full.Wolf <- glmmTMB(Wolf~  Treatment + low500_sc + pSnow_sc + LineWidth_sc + LD1250_sc + VegHt_sc + ActiveDays_sc + (1|Site) + (1|Month), data = det, zi=~1, family = nbinom1)
summary(full.Wolf)
```
### Model averaging (NOT DONE FOR 36 MONTH DATA)
  Multiple models are within 2dAIC scores of  each other, suggesting that they all explain the data equally well. As my goal is to compare Treatment effects to the effects of other covariates, I do not just want the estimates given in the top model, but rather the best possible estimates for many covariates. I will therefore model average to obtain a weighted average estimate (effect size) of covariates included in models that are within 2 dAIC of one another or within 95% confidence intervals, whichever is more conservative.
```{r, echo=FALSE}
#List of top models
Wolftop <- Models[1:5]
W.averaged <- model.avg(Wolftop)
summary(W.averaged) ## Look at full model --> parameters averaged over all models, with the coefficient set to 0 if the parameter is not present
Est.full <- W.averaged$coefficients[1,] #Estimates for the full average
CI95.full <- confint(W.averaged)
WolfEffects.CI <- as.data.frame(c("Intercept", "Lowland", "pSnow", "ActiveDays", "HumanUse", "NatRegen", "SPP", "ziIntercept", "LineDens", "VegHt", "LineWidth"))
colnames(WolfEffects.CI) <- "Predictor"
WolfEffects.CI$Estimate <- Est.full
WolfEffects.CI$CIlow <- CI95.full[, 1]
WolfEffects.CI$CI.high <- CI95.full[, 2]
```

### Predictor Effect Sizes
```{r, echo=FALSE}
library(ggplot2)
ggplot(data = WolfEffects.CI, aes( x = Predictor, y = Estimate)) + geom_point() + geom_errorbar(aes(ymin=CIlow, ymax = CI.high))+ geom_hline(yintercept = 0) + scale_x_discrete(limits=c("NatRegen", "SPP", "HumanUse", "Lowland", "pSnow", "LineDens", "LineWidth", "VegHt"))+theme_classic() + theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black", size = 12)) + theme(axis.title.x = element_text(angle = 0, colour = "black", size = 14)) + theme(axis.title.y = element_text(angle = 90, colour = "black", size = 14)) + theme(strip.text = element_text(colour = "black", size = 14)) + scale_y_continuous(limits = c(-3, 3))
```
## Exploring Interactions
  Interaction coefficients describe how much the slope of the continuous variable changes at one level of the categorical relative to the reference level
  Use top model, with pSnow and treatment interacting
```{r, echo=FALSE}
LTint <- glmmTMB(Wolf~  Treatment*pSnow_sc + low500_sc + LineWidth_sc + LD1250_sc + VegHt_sc + ActiveDays_sc + (1|Site) + (1|Month), data = det, zi=~1, family = nbinom1)
summary(LTint)
```
  This indicates that the main effect of snow on wolf detections decreases on HumanUse, NatRegen, and SPP lines relative to effect of snow on control. This would mean that the slightly negative main effect of snow on control lines has a stronger negative effect on all the other lines 
  
## Compare with AIC
```{r, echo=FALSE}
# Add interaction model to Models list
Models[["Snow-Treat"]] <- LTint
```