---
title: "Ch1_models_Wolf"
author: "Erin Tattersall"
date: "May 11, 2018"
output: word_document
---

  Based on model selection comparison of underlying distributions and zero-inflation, I chose an nbinom2 distribution for Wolf data, with zero-inflation and ActiveDays in the ZI model (see Ch1_Wolf_modelDistribution.Rmd)    
Here I will: 
1. Double check random structure using all covariates
2. Build models with environmental covariates only  
3. Build hypothesis models with line covariates + environmental  
4. Perform model selection with AIC  
5. Calculate evidence ratios (AICwt of Best Model/ AICwt of other models)  
6. Checking residuals of Top Model
7. Model Averaging?
8. Standardize parameter estimates for easy interpretation  
Previous scale analysis showed lowland habitat and linear density measured at 1750m best explained Wolf detections


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(glmmTMB)
library(bbmle) #AICtab function
library(ggplot2)
library(lmtest)
library(reshape)
library(dplyr)
library(knitr)

```
```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#Load detection data
det <- read.csv("Seismic_nov2015-apr2018.csv")

#Load lowland data
low <- read.csv("newAVIE_lowland8buffersizes.csv")

#Combine data
det$low250 <- low$low250[match(det$Site, low$CamStation)]
det$low500 <- low$low500[match(det$Site, low$CamStation)]
det$low750 <- low$low750[match(det$Site, low$CamStation)]
det$low1000 <- low$low1000[match(det$Site, low$CamStation)]
det$low1250 <- low$low1250[match(det$Site, low$CamStation)]
det$low1500 <- low$low1500[match(det$Site, low$CamStation)]
det$low1750 <- low$low1750[match(det$Site, low$CamStation)]
det$low2000 <- low$low2000[match(det$Site, low$CamStation)]

#Load linedensity data
LineDens <- read.csv("AlgarStationsLD_Lines.csv")

# Combine datasets
det$LD250 <- LineDens$X250m[match(det$Site, LineDens$CamStation)]
det$LD500 <- LineDens$X500m[match(det$Site, LineDens$CamStation)]
det$LD750 <- LineDens$X750m[match(det$Site, LineDens$CamStation)]
det$LD1000 <- LineDens$X1000m[match(det$Site, LineDens$CamStation)]
det$LD1250 <- LineDens$X1250m[match(det$Site, LineDens$CamStation)]
det$LD1500 <- LineDens$X1500m[match(det$Site, LineDens$CamStation)]
det$LD1750 <- LineDens$X1750m[match(det$Site, LineDens$CamStation)]
det$LD2000 <- LineDens$X2000m[match(det$Site, LineDens$CamStation)]


#Load line width and veg height
sp <- read.csv("Spatial_covariates.csv")

det$VegHt <- sp$VegHt[match(det$Site, sp$Site)]
det$LineWidth <- sp$LineWidth[match(det$Site, sp$Site)]

str(det)


## Visualising patterns using predict function (predicting new data, given the best-fit model)
## Need to first remove NAs from explanatory variables
# newdat <-  det[ , c(1,2,12:34)] #Naming columns in df
# newdat <- na.omit(newdat) ## Exluding NA rows, which causes lengths to differ
```
### 1. Random structure  
  Random structure was previously assessed, but here I will confirm using all model covariates

```{r, echo=FALSE, message=FALSE}
r0 <- glmmTMB(Wolf~ LineWidth + LD1250 + VegHt + low500 + Treatment + pSnow, data = det, zi=~ActiveDays,family = nbinom2)
rSite <- glmmTMB(Wolf~ LineWidth + LD1250 + VegHt + low500 + Treatment + pSnow + (1|Site), data = det,zi=~ActiveDays, family = nbinom2) 
rMonth <- glmmTMB(Wolf~ LineWidth + LD1250 + VegHt + low500 + Treatment + pSnow + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)
r2 <- glmmTMB(Wolf~ LineWidth + LD1250 + VegHt + low500 + Treatment + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays,family = nbinom2)
ICtab(r0, rSite, rMonth, r2, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)

```

## Environmental models  
Model Name  | Covariates
----------- | -------------------
E1          | None
E2          | low500 + pSnow
E3          | low500
E4          | pSnow

```{r, echo=FALSE}
E1 <- glmmTMB(Wolf~1 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#2. Global model
E2 <- glmmTMB(Wolf~low500 + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#3. Lowland only
E3 <- glmmTMB(Wolf~low500 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#4. Snow only
E4 <- glmmTMB(Wolf~pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

ICtab(E1, E2, E3, E4, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE) 
```  
  E4 and E2 have very similar model weights., with the pSnow only model coming out slightly on top. This may indicate that lowland is a 'pretending variable', or unrelated. Check deviance and parameter estimates for both models.  
```{r, echo=FALSE}
summary(E4)
summary(E2)
```  
  Deviance does not change much, and lowland habitat does not seem to have a large effect on the response variable.
  Continue modelling Line characteristics with pSnow only, as this is the most parsimonious model

## Line characteristics  
Model Name  | Covariates
----------- | -------------------
L1          | Treatment + pSnow
L2          | VegHt + pSnow
L3          | LD1250 + pSnow
L4          | LineWidth + pSnow
L5          | Treatment + LineWidth + pSnow
L6          | LineWidth + VegHt + pSnow
L7          | Treatment + LD1250 + pSnow
L8          | LD1250 + VegHt + pSnow
L9          | Treatment + VegHt + pSnow
L10         | Treatment + LineWidth + VegHt + pSnow
L11         | Treatment + LineWidth + LD1250 + pSnow
L12         | Treatment + VegHt + LD1250 + pSnow
L13         | LineWidth + VegHt + LD1250 + pSnow
L14         | Treatment + LineWidth + LD1250 + VegHt + pSnow  

```{r, echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
#1. Treatment
L1 <- glmmTMB(Wolf~Treatment + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#2. VegHt
L2 <- glmmTMB(Wolf~ VegHt + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#3. Line density
L3 <- glmmTMB(Wolf~ LD1250 + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#4. Line Width
L4 <- glmmTMB(Wolf~ LineWidth + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#5. Treatment + LineWidth
L5 <- glmmTMB(Wolf~ Treatment + LineWidth + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#6. LineWidth + VegHt
L6 <- glmmTMB(Wolf~ LineWidth + VegHt + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays,family = nbinom2)

#7. Treatment + Line density
L7 <- glmmTMB(Wolf~ Treatment + LD1250 + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#8. Line density and VegHt
L8 <- glmmTMB(Wolf~ LD1250 + VegHt + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#9. VegHt + Treatment
L9 <- glmmTMB(Wolf~ Treatment + VegHt + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#10. Treatment, LineWidth, VegHt
L10 <- glmmTMB(Wolf~ Treatment + LineWidth + VegHt + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#11. Treatment, LineWidth, Line density
L11 <- glmmTMB(Wolf~ Treatment + LineWidth + LD1250 + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#12. Treatment, Line density, VegHt
L12 <- glmmTMB(Wolf~ Treatment + VegHt + LD1250 + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#13. LineWidth, VegHt, Line density
L13 <- glmmTMB(Wolf~ LineWidth + VegHt + LD1250 + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#14. Global model - Treatment, Line density, VegHt, LineWidth
L14 <-  glmmTMB(Wolf~ Treatment + LineWidth + LD1250 + VegHt + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

WolfAIC <- ICtab(E1, E2, E3, E4, L1, L2, L3, L4, L5, L6, L7, L8, L9, L10, L11, L12, L13, L14, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
WolfAIC
```
  Six models within 2 dAIC points of each other, with model weights between 0.06 - 16%  
  LineWidth present in 3, Treatment in 2, VegHt in 2  
  
## Evidence Ratios and Cumulative model weight (calculating confidence intervals)
  
  Calculating evidence ratios (AIC wt of best model/AIC weight of others) gives:
  
```{r,echo=FALSE, results='hide'}
EvR <- function(AICwt.high, AICwt.low){
  EvR <- AICwt.high/AICwt.low
  print(EvR)
}
EvR(WolfAIC$weight[1], WolfAIC$weight[2])
WolfWt <- WolfAIC$weight
WolfER <- vector(length=17)
for(i in 2:18){
  WolfER[i-1] <- EvR(WolfWt[1], WolfWt[i])
}
```
```{r,echo=FALSE}
WolfER <- append("", WolfER)
ER <- as.data.frame(WolfER)
ER$dLogLikelihood <- WolfAIC$dLogLik
ER$dAIC <- WolfAIC$dAIC
ER$Modelweight <- WolfAIC$weight
ER$ModelNames <- c("L4", "L9", "L5", "L2", "L6", "L1", "E4", "L12", "L10", "E2", "L11", "L8", "L7", "L13", "L3", "L14", "E1", "E3")

ER$weight.cum <- rep(NA,18)
ER$weight.cum[1] <- ER$Modelweight[1]
for (i in 2:length(ER$Modelweight)){
  ER$weight.cum[i] <- ER$Modelweight[i] + ER$weight.cum[i-1]
}

ER <- ER %>% select(ModelNames, dLogLikelihood, dAIC, Modelweight, weight.cum, WolfER)
colnames(ER) <- c("ModelNames", "dLogLikelihood", "dAIC", "Modelweight", "CumulativeWeight", "EvidenceRatio")
ER

```
###Summary Output for Top Model
````{r, echo=FALSE}
summary(L4)
```


### Plotting residuals against fitted values and predicted values for all covariates
```{r, echo=FALSE}

## Residual plot for global model(L4)
op <- par(mfrow = c(1,2))
pred <- predict(L4, zitype = "response")
resid <- residuals(L4)

## Plot residuals against predicted --> diagonal lines characteristic of discrete data

{plot(pred, resid, main = "Residuals vs. Predicted", xlab = "Predicted Values", ylab = "Residuals")
abline(h = 0, lty = 2)  
lines(smooth.spline(pred, resid))}
{plot(fitted(L4), residuals(L4), main= "Residuals vs Fitted", xlab = "Fitted Values", ylab = "Residuals")
abline(h = 0, lty = 2)
lines(smooth.spline(fitted(L4), resid))}



```
