---
title: "Ch1_models_caribou"
author: "Erin Tattersall"
date: "April 27, 2018"
output: word_document
---

Based on model selection comparison of underlying distributions and zero-inflation, I chose an nbinom1 distribution for Caribou data, with zero-inflation and ActiveDays in the ZI model (see Ch1_Caribou_modelDistribution.Rmd).  
  I previously had decided to include ActiveDays in the ZI model. However, to retain the same amount of data in each model, I need to omit rows with NAs. NA rows are usually those in which cameras were inactive. Therefore, in the final dataset used in modelling, ActiveDays should have a greater effect on the count data, not the zero mass, so it should be included in the conditional model.
Here I will: 
1. Double check random structure using all covariates
2. Build models assessing Treatment effect, including other combinations of covariates to account for additional noise and compare their effect to Treatment 
4. Perform model selection with AIC  
5. Calculate evidence ratios (AICwt of Best Model/ AICwt of other models)  
6. Checking residuals of Top Model
  
Previous scale analysis showed lowland habitat and linear density measured at 1750m best explained Caribou detections


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(glmmTMB)
library(bbmle) #AICtab function
library(ggplot2)
library(lmtest)
library(reshape)
library(dplyr)
library(knitr)
library(MuMIn) #streamlining model selection

```
```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
## Set working directory in console and read.csv from there (issues with setting WD in Rmarkdown)
## Load detection data
det <- read.csv("Seismic_nov2015-2018.csv")
summary(det) ## Need to add column for month by splitting Yr_Month
det$Yr_Month2 <- det$Yr_Month
det <- separate(det, Yr_Month2, c("Year", "Month"), sep = "-", remove=TRUE)
str(det)

#Load lowland data
low <- read.csv("newAVIE_lowland8buffersizes.csv")

#Combine data
det$low250 <- low$low250[match(det$Site, low$CamStation)]
det$low500 <- low$low500[match(det$Site, low$CamStation)]
det$low750 <- low$low750[match(det$Site, low$CamStation)]
det$low1000 <- low$low1000[match(det$Site, low$CamStation)]
det$low1250 <- low$low1250[match(det$Site, low$CamStation)]
det$low1500 <- low$low1500[match(det$Site, low$CamStation)]
det$low1750 <- low$low1750[match(det$Site, low$CamStation)]
det$low2000 <- low$low2000[match(det$Site, low$CamStation)]

#Load linedensity data
LineDens <- read.csv("AlgarStationsLD_Lines.csv")

# Combine datasets
det$LD250 <- LineDens$X250m[match(det$Site, LineDens$CamStation)]
det$LD500 <- LineDens$X500m[match(det$Site, LineDens$CamStation)]
det$LD750 <- LineDens$X750m[match(det$Site, LineDens$CamStation)]
det$LD1000 <- LineDens$X1000m[match(det$Site, LineDens$CamStation)]
det$LD1250 <- LineDens$X1250m[match(det$Site, LineDens$CamStation)]
det$LD1500 <- LineDens$X1500m[match(det$Site, LineDens$CamStation)]
det$LD1750 <- LineDens$X1750m[match(det$Site, LineDens$CamStation)]
det$LD2000 <- LineDens$X2000m[match(det$Site, LineDens$CamStation)]


#Load line width and veg height
sp <- read.csv("Spatial_covariates.csv")

det$VegHt <- sp$VegHt[match(det$Site, sp$Site)]
det$LineWidth <- sp$LineWidth[match(det$Site, sp$Site)]

LT <- lm(low250_sc~Treatment, data=det)
summary(LT)

### Centring and standardizing covariates
## All continuous input variables need to be centred and standardized ((value - mean)/2SD; Gelman, 2008)
covscale <- function(covariate){
  centre <- (covariate - mean(covariate, na.rm = TRUE)) # where covariate is a vector of numeric input values for one covariate
  standardize <- centre/(2*sd(covariate, na.rm = TRUE)) # Divide centred value by 2 SD
}

summary(det$ActiveDays) #mean 18
sd(det$ActiveDays)
det$ActiveDays_sc <- covscale(det$ActiveDays)
summary(det$ActiveDays_sc)
sd(det$ActiveDays_sc)


det$pSnow_sc <- covscale(det$pSnow)
summary(det$pSnow_sc) #NAs, probably because of NAs in pSnow --> added na.rm = TRUE to function
det$pSnow_sc <- covscale(det$pSnow)
summary(det$pSnow_sc)
sd(det$pSnow_sc, na.rm = TRUE)
det$low250_sc <- covscale(det$low250)
det$low500_sc <- covscale(det$low500)
det$low750_sc <- covscale(det$low750)
det$low1000_sc <- covscale(det$low1000)
det$low1250_sc <- covscale(det$low1250)
det$low1500_sc <- covscale(det$low1500)
det$low1750_sc <- covscale(det$low1750)
det$low2000_sc <- covscale(det$low2000)
det$LD250_sc <- covscale(det$LD250)
det$LD500_sc <- covscale(det$LD500)
det$LD750_sc <- covscale(det$LD750)
det$LD1000_sc <- covscale(det$LD1000)
det$LD1250_sc <- covscale(det$LD1250)
det$LD1500_sc <- covscale(det$LD1500)
det$LD1750_sc <- covscale(det$LD1750)
det$LD2000_sc <- covscale(det$LD2000)
det$LineWidth_sc <- covscale(det$LineWidth)
det$VegHt_sc <- covscale(det$VegHt)

summary(det[ , 36:56]) #Centred means of 0


write.csv(det, "Seismic_nov2015-2018.csv")

# Omit NA rows
det <- na.omit(det)
```
### 1. Random structure and Active Days 
  Random structure was previously assessed, but here I will confirm using all model covariates. Also comparing random intercepts vs random slope 

```{r, echo=FALSE, message=FALSE}
r0 <- glmmTMB(Caribou~ LineWidth_sc + LD1750_sc + VegHt_sc + low1750_sc + Treatment + pSnow_sc + ActiveDays_sc, data = det, zi=~1,family = nbinom1)
rSite <- glmmTMB(Caribou~ LineWidth_sc + LD1750_sc + VegHt_sc + low1750_sc + Treatment + pSnow_sc + ActiveDays_sc + (1|Site), data = det, zi=~1,  family = nbinom1) 
rMonth <- glmmTMB(Caribou~ LineWidth_sc + LD1750_sc + VegHt_sc + low1750_sc + Treatment + pSnow_sc + ActiveDays_sc + (1|Month), data = det, zi=~1, family = nbinom1)
r2 <- glmmTMB(Caribou~ LineWidth_sc + LD1750_sc + VegHt_sc + low1750_sc + Treatment + pSnow_sc + ActiveDays_sc + (1|Site) + (1|Month), data = det, zi=~1, family = nbinom1)
rSiteS <- glmmTMB(Caribou~ LineWidth_sc + LD1750_sc + VegHt_sc + low1750_sc + Treatment + pSnow_sc + ActiveDays_sc + (Treatment|Site), data = det,zi=~1, family = nbinom1) 
rMonthS <- glmmTMB(Caribou~ LineWidth_sc + LD1750_sc + VegHt_sc + low1750_sc + Treatment + pSnow_sc + ActiveDays_sc +  (Treatment|Month), data = det, zi=~1, family = nbinom1)
r2S <- glmmTMB(Caribou~ LineWidth_sc + LD1750_sc + VegHt_sc + low1750_sc + Treatment + pSnow_sc + ActiveDays_sc + (Treatment|Site) + (Treatment|Month), data = det, zi=~1, family = nbinom1)
ICtab(r0, rSite, rMonth, r2, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
```  
  Random slope models fail to converge, so exclude. Continue modelling with 2 random effects.
 (note that numbered models from dredge do not correspond with numbers in table; I have listed models in order of increasing complexity, dredge did not)
 Also: ActiveDays is also fixed in all models (including NULL)

Model Name  | Covariates
----------- | -------------------
L0          | 1
L1          | Treatment
L2          | Treatment + low1750
L3          | Treatment + pSnow
L4          | Treatment + LineWidth 
L5          | Treatment + VegHt
L6          | Treatment + LD1750
L7          | Treatment + low1750 + pSnow
L8          | Treatment + low1750 + LineWidth
L9          | Treatment + low1750 + VegHt
L10         | Treatment + low1750 + LD1750
L11         | Treatment + pSnow + LineWidth
L12         | Treatment + pSnow + VegHt
L13         | Treatment + pSnow + LD1750
L14         | Treatment + LineWidth + VegHt
L15         | Treatment + LineWidth + LD1750
L16         | Treatment + VegHt + LD1750
L17         | Treatment + low1750 + pSnow + LineWidth
L18         | Treatment + low1750 + pSnow + VegHt
L19         | Treatment + low1750 + pSnow + LD1750
L20         | Treatment + low1750 + LineWidth + VegHt
L21         | Treatment + low1750 + LineWidth + LD1750
L22         | Treatment + low1750 + VegHt + LD1750
L23         | Treatment + pSnow + LineWidth + VegHt
L24         | Treatment + pSnow + LineWidth + LD1750
L24         | Treatment + pSnow + VegHt + LD1750
L25         | Treatment + LineWidth + VegHt + LD1750
L26         | Treatment + low1750 + pSnow + LineWidth + VegHt
L27         | Treatment + low1750 + pSnow + LineWidth + LD1750
L28         | Treatment + pSnow + LineWidth + VegHt + LD1750
L29         | Treatment + low1750 + LineWidth + vegHt + LD1750
L30         | Treatment + low1750 + pSnow + VegHt + LD1750
L31         | Treatment + low1750 + pSnow + LineWidth + VegHt + LD1750

```{r, echo=FALSE, message=FALSE, results='hide'}
# dredge function from MuMin generatesand evaluates model sets
global.model <- glmmTMB(Caribou~  Treatment + low1750_sc + pSnow_sc + LineWidth_sc + LD1750_sc + VegHt_sc + ActiveDays_sc + (1|Site) + (1|Month), data = det, zi=~1, family = nbinom1)

#List of all possible models including Treatment and some combination of other covariates. Runs models and returns a model selection data frame
Treat.models <- dredge(global.model = global.model, beta = "none", evaluate = TRUE, rank = "AIC", fixed = ~cond(Treatment) + cond(ActiveDays_sc), trace = TRUE) # Does not include null model
#Lists model objects
Models <- get.models(Treat.models, subset = TRUE)

## Add NULL model to list
NULLmod <- glmmTMB(Caribou~ ActiveDays_sc + (1|Site) + (1|Month), data = det, zi=~1, family = nbinom1)
Models[["Nullmod"]] <- NULLmod

names(Models)
```
```{r,echo=FALSE}

CaribouAIC <- ICtab(Models, mnames = names(Models), type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
CaribouAIC
``` 
```{r, echo=FALSE, results='hide'}
summary(Models$`14`)

## Compare estimates to those in model with unstandardized covariates
unstd.mod <- glmmTMB(Caribou~ LD1750 + low1750 + pSnow + VegHt + Treatment + (1|Site) + (1|Month), data = det, zi=~ActiveDays_sc, family = nbinom1)
summary(unstd.mod) ### Treatment coefficients are the same but continuous covariate coefficients are not. Significance is same
```
  Five models within 2 dAIC points of each other, with model weights between 9 - 22%.
    
  
## Evidence Ratios and Cumulative model weight (calculating confidence intervals)
  
  Calculating evidence ratios (AIC wt of best model/AIC weight of others) gives:
  
```{r,echo=FALSE, results='hide'}
EvR <- function(AICwt.high, AICwt.low){
  EvR <- AICwt.high/AICwt.low
  print(EvR)
}
EvR(CaribouAIC$weight[1], CaribouAIC$weight[2])
CaribouWt <- CaribouAIC$weight
CaribouER <- vector(length=32)
for(i in 2:33){
  CaribouER[i-1] <- EvR(CaribouWt[1], CaribouWt[i])
}
```
```{r,echo=FALSE}
CaribouER <- append("", CaribouER)
ER <- as.data.frame(names(Models)) ## As dredge orders models based on dAIC scores, I call names directly
colnames(ER) <- "ModelNames"
ER$dLogLikelihood <- CaribouAIC$dLogLik
ER$dAIC <- CaribouAIC$dAIC
ER$Modelweight <- CaribouAIC$weight
ER$CumulativeWeight <- rep(NA,33)
ER$CumulativeWeight[1] <- ER$Modelweight[1]
for (i in 2:length(ER$Modelweight)){
  ER$CumulativeWeight[i] <- ER$Modelweight[i] + ER$CumulativeWeight[i-1]
}
ER$EvidenceRatio <- CaribouER

ER
```
 Examining summaries for top 2 models (2dAIC)  
```{r, echo=FALSE, results='hide'}
fixef(Models$`14`)
fixef(Models$`16`)
fixef(Models$`30`)

```  
In addtion to Treatment and ActiveDays, all 3 models contain pSnow, LD and lowland. 2nd and 3rd top models contain lide width and veg height, respectively

### Pretending variables (NOT DONE for 36 month data)
  Comparing deviance of top models - if covariate does not add much, resdiual deviance will be similar across models
  
 Model                                            | Est. + SE of addtional variables             | Residual Deviance
--------------------------------------------------|----------------------------------------------|---------------------
Treat + low + pSnow + LD + ActiveDays             |                                              | 597.5
Treat + low + pSnow + ActiveDays                  |                                              | 599.8
Treat + low + LD + pSnow + VegHt + ActiveDays     | VegHt -0.85 +/- 0.88                         | 596.5
Treat + low + pSnow + VegHt + ActiveDays          | VegHt -0.80 +/- 0.85                         | 598.9
Treat + low + LD  LineWidth + ActiveDays          | LineWidth 0.21 +/- 0.44                      | 597.2

  Parameter estimates and deviance are similar, indicating all models are roughly equivalent to one another.

### Summary for full model
```{r, echo=FALSE}


## Summary for full model
full.caribou <- glmmTMB(Caribou~  Treatment + low1750_sc + pSnow_sc + LineWidth_sc + LD1750_sc + VegHt_sc + ActiveDays_sc + (1|Site) + (1|Month), data = det, zi=~1, family = nbinom1)
summary(full.caribou)

```

### Model averaging (NOT DONE FOR 36MONTH DATA)
  Multiple models are within 2dAIC scores of  each other, suggesting that they all explain the data equally well. As my goal is to compare Treatment effects to the effects of other covariates, I do not just want the estimates given in the top model, but rather the best possible estimates for many covariates. I will therefore model average to obtain a weighted average estimate (effect size) of covariates included in models that are within 2 dAIC of one another or within 95% confidence intervals, whichever is more conservative.
```{r, echo=FALSE}
#List of top models
Cariboutop <- Models[1:5]
Caribou.averaged <- model.avg(Cariboutop)
summary(Caribou.averaged) ## Look at full model --> parameters averaged over all models, with the coefficient set to 0 if the parameter is not present
Est.full <- Caribou.averaged$coefficients[1,] #Estimates for the full average
CI95.full <- confint(Caribou.averaged)
CaribouEffects.CI <- as.data.frame(c("Intercept", "LineDens", "Lowland", "pSnow", "ActiveDays", "HumanUse", "NatRegen", "SPP", "ziIntercept", "VegHt",  "LineWidth")) #Reorder according to order of averaged coefs
colnames(CaribouEffects.CI) <- "Predictor"
CaribouEffects.CI$Estimate <- Est.full
CaribouEffects.CI$CIlow <- CI95.full[, 1]
CaribouEffects.CI$CI.high <- CI95.full[, 2]
```
### Predictor Effect Sizes
```{r, echo=FALSE}
library(ggplot2)
ggplot(data = CaribouEffects.CI, aes( x = Predictor, y = Estimate)) + geom_point() + geom_errorbar(aes(ymin=CIlow, ymax = CI.high))+ geom_hline(yintercept = 0) + scale_x_discrete(limits=c("NatRegen", "SPP", "HumanUse", "Lowland", "pSnow", "LineDens", "LineWidth", "VegHt"))+theme_classic() + theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black", size = 12)) + theme(axis.title.x = element_text(angle = 0, colour = "black", size = 14)) + theme(axis.title.y = element_text(angle = 90, colour = "black", size = 14)) + theme(strip.text = element_text(colour = "black", size = 14)) + scale_y_continuous(limits = c(-5, 5))
```

## Exploring Interactions
  Interaction coefficients describe how much the slope of the continuous variable changes at one level of the categorical relative to the reference level
  Use top model, with lowland and treatment interacting
```{r, echo=FALSE}
LTint <- glmmTMB(Caribou~Treatment*low1750_sc + pSnow_sc + LD1750_sc + ActiveDays_sc + (1|Site) + (1|Month), data = det, zi=~1, family = nbinom1)
summary(LTint)
```
  Although not significant, this indicates that the main effect of lowland habitat on caribou detections decreases on HumanUse, NatRegen, and SPP lines relative to effect of lowland on control (HumanUse almost significant)
