---
title: "Ch1_Moose_model"
author: "Erin Tattersall"
date: "May 13, 2018"
output: word_document
---


  Based on model selection comparison of underlying distributions and zero-inflation, I chose an nbinom2 distribution for Moose data, with zero-inflation and ActiveDays in the ZI model (see Ch1_Moose_modelDistribution.Rmd)    
Here I will: 
1. Double check random structure using all covariates
2. Build models with environmental covariates only  
3. Build hypothesis models with line covariates + environmental  
4. Perform model selection with AIC  
5. Calculate evidence ratios (AICwt of Best Model/ AICwt of other models)  
6. Checking residuals of Top Model
7. Model Averaging?
8. Standardize parameter estimates for easy interpretation  
Previous scale analysis showed lowland habitat and linear density measured at 1750m best explained Moose detections


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(glmmTMB)
library(bbmle) #AICtab function
library(ggplot2)
library(lmtest)
library(reshape)
library(dplyr)
library(knitr)

```
```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#Load detection data
det <- read.csv("Seismic_nov2015-apr2018.csv")

#Load lowland data
low <- read.csv("newAVIE_lowland8buffersizes.csv")

#Combine data
det$low250 <- low$low250[match(det$Site, low$CamStation)]
det$low500 <- low$low500[match(det$Site, low$CamStation)]
det$low750 <- low$low750[match(det$Site, low$CamStation)]
det$low1000 <- low$low1000[match(det$Site, low$CamStation)]
det$low1250 <- low$low1250[match(det$Site, low$CamStation)]
det$low1500 <- low$low1500[match(det$Site, low$CamStation)]
det$low1750 <- low$low1750[match(det$Site, low$CamStation)]
det$low2000 <- low$low2000[match(det$Site, low$CamStation)]

#Load linedensity data
LineDens <- read.csv("AlgarStationsLD_Lines.csv")

# Combine datasets
det$LD250 <- LineDens$X250m[match(det$Site, LineDens$CamStation)]
det$LD500 <- LineDens$X500m[match(det$Site, LineDens$CamStation)]
det$LD750 <- LineDens$X750m[match(det$Site, LineDens$CamStation)]
det$LD1000 <- LineDens$X1000m[match(det$Site, LineDens$CamStation)]
det$LD1250 <- LineDens$X1250m[match(det$Site, LineDens$CamStation)]
det$LD1500 <- LineDens$X1500m[match(det$Site, LineDens$CamStation)]
det$LD750 <- LineDens$X1750m[match(det$Site, LineDens$CamStation)]
det$LD2000 <- LineDens$X2000m[match(det$Site, LineDens$CamStation)]


#Load line width and veg height
sp <- read.csv("Spatial_covariates.csv")

det$VegHt <- sp$VegHt[match(det$Site, sp$Site)]
det$LineWidth <- sp$LineWidth[match(det$Site, sp$Site)]



## Visualising patterns using predict function (predicting new data, given the best-fit model)
## Need to first remove NAs from explanatory variables
# newdat <-  det[ , c(1,2,12:34)] #Naming columns in df
# newdat <- na.omit(newdat) ## Exluding NA rows, which causes lengths to differ
```
### 1. Random structure  
  Random structure was previously assessed, but here I will confirm using all model covariates

```{r, echo=FALSE}
r0 <- glmmTMB(Moose~ LineWidth + LD1250 + VegHt + low250 + Treatment + pSnow + Dist2Water_km, data = det, zi=~ActiveDays,family = nbinom2)
rSite <- glmmTMB(Moose~ LineWidth + LD1250 + VegHt + low250 + Treatment + pSnow + Dist2Water_km + (1|Site), data = det,zi=~ActiveDays, family = nbinom2) 
rMonth <- glmmTMB(Moose~ LineWidth + LD1250 + VegHt + low250 + Treatment + pSnow + Dist2Water_km + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)
r2 <- glmmTMB(Moose~ LineWidth + LD1250 + VegHt + low250 + Treatment + pSnow + Dist2Water_km + (1|Site) + (1|Month), data = det, zi=~ActiveDays,family = nbinom2)
ICtab(r0, rSite, rMonth, r2, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
```

## Environmental models  
Model Name  | Covariates
----------- | -------------------
E1          | None
E2          | low250 + pSnow + Dist2Water_km
E3          | low250 + pSnow
E4          | pSnow + Dist2Water_km
E5          | low250 + Dist2Water_km
E6          | low250
E7          | pSnow
E8          | Dist2Water_km

```{r, echo=FALSE}
E1 <- glmmTMB(Moose~1 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#2. Global model
E2 <- glmmTMB(Moose~low250 + pSnow + Dist2Water_km + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#3. Lowland + pSnow
E3 <- glmmTMB(Moose~low250 + pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#4. Snow + Water
E4 <- glmmTMB(Moose~pSnow + Dist2Water_km + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#E5. low + Water
E5 <- glmmTMB(Moose~low250 + Dist2Water_km + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#E6. Lowland only
E6 <- glmmTMB(Moose~low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#E7. pSnow only
E7 <- glmmTMB(Moose~pSnow + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#E8. Water only
E8 <- glmmTMB(Moose~Dist2Water_km + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

ICtab(E1, E2, E3, E4, E5, E6, E7, E8, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE) 
``` 
    E6 has the most model weight and is the only model that performs better than the null, although only slightly. Examining shows that even this model does not have much explanatory power. I will continue to use only Lowland habitat.
    

## Line characteristics  
Model Name  | Covariates
----------- | -------------------
L1          | Treatment + low250 
L2          | VegHt + low250 
L3          | LD1250 + low250
L4          | LineWidth + low250
L5          | Treatment + LineWidth + low250
L6          | LineWidth + VegHt + low250
L7          | Treatment + LD1250 + low250
L8          | LD1250 + VegHt + low250
L9          | Treatment + VegHt + low250
L10         | Treatment + LineWidth + VegHt + low250
L11         | Treatment + LineWidth + LD1250 + low250
L12         | Treatment + VegHt + LD1250 + low250
L13         | LineWidth + VegHt + LD1250 + low250
L14         | Treatment + LineWidth + LD1250 + VegHt + low250 

```{r, echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
#1. Treatment
L1 <- glmmTMB(Moose~Treatment + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#2. VegHt
L2 <- glmmTMB(Moose~ VegHt + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#3. Line density
L3 <- glmmTMB(Moose~ LD1250 + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#4. Line Width
L4 <- glmmTMB(Moose~ LineWidth + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#5. Treatment + LineWidth
L5 <- glmmTMB(Moose~ Treatment + LineWidth + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#6. LineWidth + VegHt
L6 <- glmmTMB(Moose~ LineWidth + VegHt + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays,family = nbinom2)

#7. Treatment + Line density
L7 <- glmmTMB(Moose~ Treatment + LD1250 + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#8. Line density and VegHt
L8 <- glmmTMB(Moose~ LD1250 + VegHt + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#9. VegHt + Treatment
L9 <- glmmTMB(Moose~ Treatment + VegHt + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#10. Treatment, LineWidth, VegHt
L10 <- glmmTMB(Moose~ Treatment + LineWidth + VegHt + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#11. Treatment, LineWidth, Line density
L11 <- glmmTMB(Moose~ Treatment + LineWidth + LD1250 + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#12. Treatment, Line density, VegHt
L12 <- glmmTMB(Moose~ Treatment + VegHt + LD1250 + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#13. LineWidth, VegHt, Line density
L13 <- glmmTMB(Moose~ LineWidth + VegHt + LD1250 + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

#14. Global model - Treatment, Line density, VegHt, LineWidth
L14 <-  glmmTMB(Moose~ Treatment + LineWidth + LD1250 + VegHt + low250 + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)

MooseAIC <- ICtab(E1, E2, E3, E4, E5, E6, E7, E8, L1, L2, L3, L4, L5, L6, L7, L8, L9, L10, L11, L12, L13, L14, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
MooseAIC
```
  Four models within 2 dAIC points of each other, with model weights between 13 - 36%. Treatment in second model.  
  
    
  
## Evidence Ratios and Cumulative model weight (calculating confidence intervals)
  
  Calculating evidence ratios (AIC wt of best model/AIC weight of others) gives:
  
```{r,echo=FALSE, results='hide'}
EvR <- function(AICwt.high, AICwt.low){
  EvR <- AICwt.high/AICwt.low
  print(EvR)
}
EvR(MooseAIC$weight[1], MooseAIC$weight[2])
MooseWt <- MooseAIC$weight
MooseER <- vector(length=21)
for(i in 2:22){
  MooseER[i-1] <- EvR(MooseWt[1], MooseWt[i])
}
```
```{r,echo=FALSE}
MooseER <- append("", MooseER)
ER <- as.data.frame(MooseER)
ER$dLogLikelihood <- MooseAIC$dLogLik
ER$dAIC <- MooseAIC$dAIC
ER$Modelweight <- MooseAIC$weight
ER$ModelNames <- c("L6", "L13", "L4", "L2", "L8", "L10", "L9", "L14", "L12", "L5", "L11","E6", "E1", "L3", "E3","E5", "E8", "E7", "E2", "E4", "L1", "L7")
ER$weight.cum <- rep(NA,22)
ER$weight.cum[1] <- ER$Modelweight[1]
for (i in 2:length(ER$Modelweight)){
  ER$weight.cum[i] <- ER$Modelweight[i] + ER$weight.cum[i-1]
}

ER <- ER %>% select(ModelNames, dLogLikelihood, dAIC, Modelweight, weight.cum, MooseER)
colnames(ER) <- c("ModelNames", "dLogLikelihood", "dAIC", "Modelweight", "CumulativeWeight", "EvidenceRatio")
ER

```
###Summary Output for Top Model
````{r, echo=FALSE}
summary(L6)
```


### Plotting residuals against fitted values and predicted values for all covariates
```{r, echo=FALSE}

## Residual plot for global model(L6)
op <- par(mfrow = c(1,2))
pred <- predict(L6, zitype = "response")
resid <- residuals(L6)

## Plot residuals against predicted --> diagonal lines characteristic of discrete data

{plot(pred, resid, main = "Residuals vs. Predicted", xlab = "Predicted Values", ylab = "Residuals")
abline(h = 0, lty = 2)  
lines(smooth.spline(pred, resid))}
{plot(fitted(L6), residuals(L6), main= "Residuals vs Fitted", xlab = "Fitted Values", ylab = "Residuals")
abline(h = 0, lty = 2)
lines(smooth.spline(fitted(L6), resid))}



```