---
title: "Ch3_DataExploration"
author: "Erin Tattersall"
date: "September 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("C:/Users/ETattersall/Desktop/Algar_Cam_Traps/Algar_Camera_Traps/Data"))
library(ggplot2) #for plotting magic
library(dplyr) #for data management convenience
library(tidyr) #for data management (gather function)
library(fmsb)
```

 Data Exploration
   A protocol for checking input variables for outliers, collinearities, interactions, etc, as outlined by Zuur et al. (2010)
  Register all data --> occurrence data, habitat variables, snow and line density (all should now be included in occurrence csvs)
```{r, echo = FALSE}

Occ <- read.csv("Algar60_speciesOccurrence.csv")
Bears <- read.csv("Algar60_speciesOccurrence_SUMMER.csv") ## Truncated for summer -- for Black bears


str(Occ)

str(Bears)

Occ$X <- NULL
Bears$X <- NULL

## Scaled input variables
## covscale function
covscale <- function(covariate){
  centre <- (covariate - mean(covariate, na.rm = TRUE)) # where covariate is a vector of numeric input values for one covariate
  standardize <- centre/(2*sd(covariate, na.rm = TRUE)) # Divide centred value by 2 SD
}

Occ_sc <- cbind.data.frame(Occ[ ,1:17], lapply(Occ[ , 18:23], covscale))



```

## 1. Check outliers and homogeneity of variance - X and Y data
### Species occurrences (note that all will be heavily zero-inflated)
```{r}
## Gather all species columns together (Occ)
O1 <- gather(data = Occ, key = Species, value = Occurrence, 5:14)
## Histograms --> don't show data well
spocc <- ggplot(data= O1, aes(Occurrence)) + geom_histogram(color = ("black"), fill = "transparent", binwidth = 1) + facet_wrap(~Species) +theme_classic()
spocc
```
  Species Occurrence Tables
```{r}
colSums(Occ[,5:14])
```
  Zeroes-Count Table
```{r}
colSums(Occ[,5:14]==0)
```
  Occurrences by Site --> spatial maps would be better, but generally shows Occurrence spread across sites
  Of the predators, Coyote occurrences are most discretized to certain sites.
  Prey: Squirrel is most limiting --> lump Hare + Squirrel in 'Prey' category?
```{r}
sitocc <- ggplot(data = O1, aes(x = Site, y = Occurrence)) + geom_point() + facet_wrap(~Species) + geom_jitter()
sitocc
```
### Habitat variables and Linear Densities
```{r}
## Gather all Habitat variables 
H1 <- gather(data = Occ, key = Habitat, value = propCover, 18:21)

bp <- ggplot(data=H1, aes(x = Habitat, y = propCover, fill = Habitat)) + geom_boxplot() +theme_classic() + theme(legend.position = "none")
bp
```
  pOpen has a few outliers --> does standardizing/scaling help?
```{r}
## Gather all Habitat variables 
H2 <- gather(data = Occ_sc, key = Habitat, value = propCover, 18:21)

bp2 <- ggplot(data=H2, aes(x = Habitat, y = propCover, fill = Habitat)) + geom_boxplot() +theme_classic() + theme(legend.position = "none")
bp2
```
  Standardizes means and variance (?) but outliers remain the same. Okay to leave (not outrageously outlying)
  
#### Bears
```{r}
bearOpen <- ggplot(data = Bears, aes(x = "", y = pOpen250)) + geom_boxplot() + theme_classic()
bearOpen
```
### Linear Densities (1500 and 1750 m)
```{r}
H1 <- gather(data = Occ, key = Scale, value = LineDens, 22:23)

bp <- ggplot(data=H1, aes(x = Scale, y = LineDens, fill = Scale)) + geom_boxplot() +theme_classic() + theme(legend.position = "none")
bp

```
### Snow Presence --> Roughly equal presences and absences, 431 NAs (allowable within 32 000 observations)
```{r}
S <- ggplot(data= Occ, aes(Snow)) + geom_histogram(binwidth=1, color = "black", fill = "transparent") + theme_classic()
S
```
```{r}
summary(Occ$Snow)
```
## Homogeneity of variance -- standardized and scaled predictors
```{r}
H2 <- gather(data = Occ_sc, key = Predictor, value = Value, 18:23)

bp2 <- ggplot(data=H2, aes(x = Predictor, y = Value, fill = Predictor)) + geom_boxplot() +theme_classic()
bp2

```
  Species occurrence predictors and Snow are binomial presence/absence, where the reference value is 0 (absence)
## Collinearities
### Lynx
  Possible collinearities between LowCon and UpCon
```{r}
## Lynx predictors --> Wolf, Coyote, Hare, Squirrel, LowCon1500, UpCon1500, pOpen1500, Snow, LD1750
pairs(Occ[ , c(9,11,12,14,18,19,20,23,24)])
```
#### Variance Inflation Factors
  All ~1, no significant collinearity
```{r}
## Test an additive model of all possible input predictors for one hypothesis
L1 <-lm(Lynx~Wolf + Snow + LD1750 + LowCon1500 + UpCon1500 + pOpen1500, data = Occ) 
VIF(L1)
L2 <- lm(Lynx~Coyote + Snow + LD1750 + LowCon1500 + UpCon1500 + pOpen1500, data = Occ)
VIF(L2)
L3 <- lm(Lynx~Hare + Squirrel + Snow + LD1750 + LowCon1500 + UpCon1500 + pOpen1500, data = Occ)
VIF(L3)
```
### Coyote
```{r}
## Coyote predictors --> Wolf, Lynx, Deer, Hare, Squirrel, pOpen1750, Snow, LD1500
pairs(Occ[ , c(5, 9,10, 11,12,14,21,22,24)])

```

#### Variance Inflation Factors
  All ~1, no significant collinearities
```{r}
## Test an additive model of all possible input predictors for one hypothesis
C1 <-lm(Coyote~Wolf + Snow + LD1500 + pOpen1750, data = Occ) 
VIF(C1)
C2 <- lm(Coyote~Lynx + Snow + LD1500 + pOpen1750, data = Occ)
VIF(C2)
C3 <- lm(Coyote~ WTDeer + Hare + Squirrel + Snow + LD1500 + pOpen1750, data = Occ)
VIF(C3)
```

### Black bears
```{r}
## Black bear predictors --> Wolf, Deer, Moose, Caribou, pOpen250, Snow, LD1500
pairs(Bears[, c(5,7,8,11,18,19)])
```
#### Variance Inflation Factors
  All ~1, no significant collinearities
```{r}
## Test an additive model of all possible input predictors for one hypothesis
B1 <-lm(Blackbear~Wolf + LD1500 + pOpen250, data = Bears) 
VIF(B1)
B2 <-lm(Blackbear~WTDeer + Caribou + Moose + LD1500 + pOpen250, data = Bears)
VIF(B2)

```
