---
title: "Ch3_DataExploration"
author: "Erin Tattersall"
date: "September 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("C:/Users/ETattersall/Desktop/Algar_Cam_Traps/Algar_Camera_Traps/Data"))
library(ggplot2) #for plotting magic
library(dplyr) #for data management convenience
library(tidyr) #for data management (gather function)
library(fmsb)
```

 Data Exploration
   A protocol for checking input variables for outliers, collinearities, interactions, etc, as outlined by Zuur et al. (2010)

# Habitat covariates and linear density (checking collinearities of LD will be done after scale analysis to check if top LD scale is collinear with any variables in core models)
```{r, echo = FALSE}

Occ <- read.csv("Algar60_speciesOccurrence.csv")
Bears <- read.csv("Algar60_speciesOccurrence_SUMMER.csv") ## Truncated for summer -- for Black bears

## Significant variables for habitat and LD should already be added to Occ and Bears
Hab <- read.csv("Algar_HabitatData_8scales.csv") 
Lines <- read.csv("AlgarStationLineDensity_8scales.csv")
str(Occ)
str(Hab)
str(Bears)
str(Lines)
Occ$X <- NULL
Bears$X <- NULL
Hab$X <- NULL
Lines$X <- NULL


### Snow Presence/Absence
Snow <- read.csv("SnowPresence_daily.csv")
str(Snow)
## Remove OffLine Sites -- find first row number of Algar61
head(which(Snow$Station=="Algar61")) ##3158

Snow <- Snow[1:32157,]
table(Snow$Station) ## Only includes Algar 1-60
## Now snow is shorter than Occ --> missing inactive days?

## Match Snow to Occ (should include NAs)


```

## 1. Check outliers
```{r}
## Gather all habitat variables of same scale together (just do for 250 m for now)
d250 <- gather(data = Hab, key = HabitatType, value = propCover, c(7,9,10,11,54))
d250 <- d250[,57:58] ## Isolate scale of interest
bp250 <- ggplot(data=d250, aes(x = HabitatType, y = propCover, fill = HabitatType)) + geom_boxplot() +theme_classic() + theme(legend.position = "none")
bp250
```
  A few uncommonly high UpDecid, two low pOpen.
  
## Collinearities
```{r}
## 250 m Pairwise plots (Black bear)
pairs(Hab[, c(7,9,10,11,54)]) ## subset for columns of  1250 m habitat variables (do each scale separately so its not crazy big)
```
```{r}
## 1500 m Pairwise plot (Lynx)
pairs(Hab[ , c(36,37,39,40,41,59)])

```
```{r}
## 1750 m Pairwise plot (Coyote)
pairs(Hab[ , c(42,43,45,46,47,60)])

```
### Variance Inflation Factors (VIF)
  A VIF of 1 = safely discount correlation
#### Black bears
```{r, echo = FALSE}
# req. response and predictors on same df

Bears250 <- Bears


Bears250$LowCon <- Hab$LowCon250[match(Bears250$Site, Hab$CamStation)]
Bears250$Tamarack <- Hab$Tamarack250[match(Bears250$Site, Hab$CamStation)]
Bears250$UpCon <- Hab$UpCon250[match(Bears250$Site, Hab$CamStation)]
Bears250$UpDecid <- Hab$UpDecid250[match(Bears250$Site, Hab$CamStation)]
Bears250$pOpen <- Hab$pOpen250[match(Bears250$Site, Hab$CamStation)]

Occ1500 <- Occ


Occ1500$LowCon <- Hab$LowCon1500[match(Occ1500$Site, Hab$CamStation)]
Occ1500$LowDecid <- Hab$LowDecid1500[match(Occ1500$Site, Hab$CamStation)]
Occ1500$Tamarack <- Hab$Tamarack1500[match(Occ1500$Site, Hab$CamStation)]
Occ1500$UpCon <- Hab$UpCon1500[match(Occ1500$Site, Hab$CamStation)]
Occ1500$UpDecid <- Hab$UpDecid1500[match(Occ1500$Site, Hab$CamStation)]
Occ1500$pOpen <- Hab$pOpen1500[match(Occ1500$Site, Hab$CamStation)]

Occ1750 <- Occ


Occ1750$LowCon <- Hab$LowCon1750[match(Occ1750$Site, Hab$CamStation)]
Occ1750$LowDecid <- Hab$LowDecid1750[match(Occ1750$Site, Hab$CamStation)]
Occ1750$Tamarack <- Hab$Tamarack1750[match(Occ1750$Site, Hab$CamStation)]
Occ1750$UpCon <- Hab$UpCon1750[match(Occ1750$Site, Hab$CamStation)]
Occ1750$UpDecid <- Hab$UpDecid1750[match(Occ1750$Site, Hab$CamStation)]
Occ1750$pOpen <- Hab$pOpen1750[match(Occ1750$Site, Hab$CamStation)]
```
```{r}
lm.Bear <-lm(Blackbear~LowCon + Tamarack + UpCon + UpDecid + pOpen, data = Bears250) 
VIF(lm.Bear)
```
#### Lynx
```{r}
lm.Lynx <-lm(Lynx~LowCon + LowDecid + Tamarack + UpCon + UpDecid + pOpen, data = Occ1500) 
VIF(lm.Lynx)
```
#### Coyote
```{r}
lm.Coyote <-lm(Coyote~LowCon + LowDecid + Tamarack + UpCon + UpDecid + pOpen, data = Occ1750) 
VIF(lm.Coyote)
```