---
title: "Ch3_LineDens_scaleanalysis"
output: html_notebook
---

Scale analysis for linear density by including Linear Density measured at 8 different scales in the core model already built for each species.

1. Add line density to core model -- 8 candidate models per species.
2. Model selection.
3. Check collinearities (should be none)

```{r, message=FALSE, warning=FALSE}
library(tidyr)		# for data formatting functions
library(dplyr)
library(glmmTMB)
library(bbmle)

```

```{r, message=FALSE, warning=FALSE}
setwd("C:/Users/ETattersall/Desktop/Algar_Cam_Traps/Algar_Camera_Traps/Data") ## NOTE: setwd() needs to be set in the R env., separately from the R notebook environment (copy past command into console)
getwd()

Occ <- read.csv("Algar60_speciesOccurrence.csv")
Bears <- read.csv("Algar60_speciesOccurrence_SUMMER.csv")
##Significant habitat variables didn't save for some reason
Lines <- read.csv("AlgarStationLineDensity_8scales.csv")

str(Occ)
str(Bears)
Occ$X.2 <- NULL
Occ$X.1 <- NULL
Occ$X <- NULL

Bears$X.1 <- NULL
Bears$X <- NULL

## Attach LD data to Occ and Bears
Occ$LD250 <- Lines$X250m[match(Occ$Site, Lines$CamStation)]
Occ$LD500 <- Lines$X500m[match(Occ$Site, Lines$CamStation)]
Occ$LD750 <- Lines$X750m[match(Occ$Site, Lines$CamStation)]
Occ$LD1000 <- Lines$X1000m[match(Occ$Site, Lines$CamStation)]
Occ$LD1250 <- Lines$X1250m[match(Occ$Site, Lines$CamStation)]
Occ$LD1500 <- Lines$X1500m[match(Occ$Site, Lines$CamStation)]
Occ$LD1750 <- Lines$X1750m[match(Occ$Site, Lines$CamStation)]
Occ$LD2000 <- Lines$X2000m[match(Occ$Site, Lines$CamStation)]

Bears$LD250 <- Lines$X250m[match(Bears$Site, Lines$CamStation)]
Bears$LD500 <- Lines$X500m[match(Bears$Site, Lines$CamStation)]
Bears$LD750 <- Lines$X750m[match(Bears$Site, Lines$CamStation)]
Bears$LD1000 <- Lines$X1000m[match(Bears$Site, Lines$CamStation)]
Bears$LD1250 <- Lines$X1250m[match(Bears$Site, Lines$CamStation)]
Bears$LD1500 <- Lines$X1500m[match(Bears$Site, Lines$CamStation)]
Bears$LD1750 <- Lines$X1750m[match(Bears$Site, Lines$CamStation)]
Bears$LD2000 <- Lines$X2000m[match(Bears$Site, Lines$CamStation)]


#### Standardize and scale input variables FIRST
## covscale function
covscale <- function(covariate){
  centre <- (covariate - mean(covariate, na.rm = TRUE)) # where covariate is a vector of numeric input values for one covariate
  standardize <- centre/(2*sd(covariate, na.rm = TRUE)) # Divide centred value by 2 SD
}


## Apply covscale to input variables in Occ and Bears
Occ_sc <- cbind.data.frame(Occ[ ,1:17], lapply(Occ[ , 18:29], covscale))
Bears_sc <- cbind.data.frame(Bears[ ,1:17], lapply(Bears[ , 18:26], covscale))
```

Lynx: core model is Lynx~LowCon + UpCon + pOpen at 1500m
```{r,message=FALSE, error=FALSE, warning=FALSE}
## Register core model for comparison, then 8 models that only change in the scale at which LD is measured
Sys.time()
L0 <- glmmTMB(Lynx~LowCon1500 + UpCon1500 + pOpen1500 + (1|Site), data=Occ, family = "binomial")

L250 <- glmmTMB(Lynx~LowCon1500 + UpCon1500 + pOpen1500 + LD250 + (1|Site), data=Occ, family = "binomial")

L500 <- glmmTMB(Lynx~LowCon1500 + UpCon1500 + pOpen1500 + LD500 + (1|Site), data=Occ, family = "binomial")

L750 <- glmmTMB(Lynx~LowCon1500 + UpCon1500 + pOpen1500 + LD750 + (1|Site), data=Occ, family = "binomial")

L1000 <- glmmTMB(Lynx~LowCon1500 + UpCon1500 + pOpen1500 + LD1000 + (1|Site), data=Occ, family = "binomial")

L1250 <- glmmTMB(Lynx~LowCon1500 + UpCon1500 + pOpen1500 + LD1250 + (1|Site), data=Occ, family = "binomial")

L1500 <- glmmTMB(Lynx~LowCon1500 + UpCon1500 + pOpen1500 + LD1500 + (1|Site), data=Occ, family = "binomial")

L1750 <- glmmTMB(Lynx~LowCon1500 + UpCon1500 + pOpen1500 + LD1750 + (1|Site), data=Occ, family = "binomial")

L2000 <- glmmTMB(Lynx~LowCon1500 + UpCon1500 + pOpen1500 + LD2000 + (1|Site), data=Occ, family = "binomial")
Sys.time()
```
  Results for Lynx
```{r, warning=FALSE, error=FALSE}
Lynx.AIC <- ICtab(L0, L250, L500, L750 ,L1000, L1250,L1500,L1750,L2000,type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
Lynx.AIC
summary(L1750)
```
```{r, warning=FALSE, error=FALSE}
### Plotting model weights (ratio of AIC of one model to AIC of top model)
# Plotting model weights for each scale to determine best scale
class(Lynx.AIC) <- "data.frame"


Lynx.AIC$scale <- c("1750", "2000", "1000", "1250", "1500", "750", "500","NULL", "250") #ordered according to ICtab 

#Remove NULL row
tab <- Lynx.AIC %>% filter(scale != "NULL")
str(tab)
#Convert to numeric
tab$scale <- as.numeric(tab$scale)

##Save Lynx.AIC table for future figures (move to Figures folder in Ch.3_Interactions)
write.csv(tab, "LDscaleanalysis_Lynx.csv")


op <- par(mar = c(6,6,5,3) + 0.2)
plot(tab$scale, tab$weight, xlim=range(tab$scale), ylim=c(0,1), xlab = "", ylab = "", pch=20, cex = 4, cex.axis = 2, cex.lab = 4)
lines(tab$scale[order(tab$scale)], tab$weight[order(tab$scale)], xlim=range(tab$scale), ylim=c(0,1))
title("Lynx", line = -4, cex.main = 5)
title(xlab = "Scale (m)", line = 4, cex.lab = 4)
title(ylab = "AIC weight", cex.lab = 4)
### Having trouble running full plotting code in R Notebook. Copied to script

```
```{r, warning=FALSE, error=FALSE}

summary(L1750)
```

Coyote: core model is Coyote ~ pOpen1750
```{r, ,message=FALSE, error=FALSE, warning=FALSE}
## Register core model for comparison, then 8 models that only change in the scale at which LD is measured
Sys.time()
C0 <- glmmTMB(Coyote~ pOpen1750 + (1|Site), data=Occ, family = "binomial")

C250 <- glmmTMB(Coyote~ pOpen1750 + LD250 + (1|Site), data=Occ, family = "binomial")

C500 <- glmmTMB(Coyote~ pOpen1750 + LD500 + (1|Site), data=Occ, family = "binomial")

C750 <- glmmTMB(Coyote~pOpen1750 + LD750 + (1|Site), data=Occ, family = "binomial")

C1000 <- glmmTMB(Coyote~pOpen1750 + LD1000 + (1|Site), data=Occ, family = "binomial")

C1250 <- glmmTMB(Coyote~pOpen1750 + LD1250 + (1|Site), data=Occ, family = "binomial")

C1500 <- glmmTMB(Coyote~pOpen1750 + LD1500 + (1|Site), data=Occ, family = "binomial")

C1750 <- glmmTMB(Coyote~ pOpen1750 + LD1750 + (1|Site), data=Occ, family = "binomial")

C2000 <- glmmTMB(Coyote~ pOpen1750 + LD2000 + (1|Site), data=Occ, family = "binomial")
Sys.time()
```
  Results for Coyote
```{r, warning=FALSE, error=FALSE}
Coyote.AIC <- ICtab(C0, C250, C500, C750 ,C1000, C1250,C1500,C1750,C2000, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
Coyote.AIC
```
```{r, warning=FALSE, error=FALSE}
### Plotting model weights (ratio of AIC of one model to AIC of top model)
# Plotting model weights for each scale to determine best scale
class(Coyote.AIC) <- "data.frame"


Coyote.AIC$scale <- c("1500", "1750", "2000","1250", "1000", "750", "500", "NULL", "250") #ordered according to ICtab 

#Remove NULL row
tab <- Coyote.AIC %>% filter(scale != "NULL")
str(tab)
#Convert to numeric
tab$scale <- as.numeric(tab$scale)

##Save Coyote.AIC table for future figures (move to Figures folder in Ch.3_Interactions)
write.csv(tab, "LDscaleanalysis_Coyote.csv")

op <- par(mar = c(6,6,5,3) + 0.2)
plot(tab$scale, tab$weight, xlim=range(tab$scale), ylim=c(0,1), xlab = "", ylab = "", pch=20, cex = 4, cex.axis = 2, cex.lab = 4)
lines(tab$scale[order(tab$scale)], tab$weight[order(tab$scale)], xlim=range(tab$scale), ylim=c(0,1))
title("Coyote", line = -4, cex.main = 5)
title(xlab = "Scale (m)", line = 4, cex.lab = 4)
title(ylab = "AIC weight", cex.lab = 4)
```
```{r, warning=FALSE, error=FALSE}

summary(C1500)
```

Blackbear: core model is Blackbear ~ pOpen250
```{r, ,message=FALSE, error=FALSE, warning=FALSE}
## Register core model for comparison, then 8 models that only change in the scale at which LD is measured
Sys.time()
B0 <- glmmTMB(Blackbear~ pOpen250 + (1|Site), data=Bears, family = "binomial")

B250 <- glmmTMB(Blackbear~ pOpen250 + LD250 + (1|Site), data=Bears, family = "binomial")

B500 <- glmmTMB(Blackbear~ pOpen250 + LD500 + (1|Site), data=Bears, family = "binomial")

B750 <- glmmTMB(Blackbear~pOpen250 + LD750 + (1|Site), data=Bears, family = "binomial")

B1000 <- glmmTMB(Blackbear~pOpen250 + LD1000 + (1|Site), data=Bears, family = "binomial")

B1250 <- glmmTMB(Blackbear~pOpen250 + LD1250 + (1|Site), data=Bears, family = "binomial")

B1500 <- glmmTMB(Blackbear~pOpen250 + LD1500 + (1|Site), data=Bears, family = "binomial")

B1750 <- glmmTMB(Blackbear~ pOpen250 + LD1750 + (1|Site), data=Bears, family = "binomial")

B2000 <- glmmTMB(Blackbear~ pOpen250 + LD2000 + (1|Site), data=Bears, family = "binomial")
Sys.time()
```
  Results for Blackbear
```{r, warning=FALSE, error=FALSE}
Blackbear.AIC <- ICtab(B0, B250, B500, B750 ,B1000, B1250,B1500,B1750,B2000, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
Blackbear.AIC
```
```{r, warning=FALSE, error=FALSE}
### Plotting model weights (ratio of AIC of one model to AIC of top model)
# Plotting model weights for each scale to determine best scale
class(Blackbear.AIC) <- "data.frame"


Blackbear.AIC$scale <- c("1500", "1750", "2000", "1250", "1000", "750", "NULL", "250", "500") #ordered according to ICtab 

#Remove NULL row
tab <- Blackbear.AIC %>% filter(scale != "NULL")
str(tab)
#Convert to numeric
tab$scale <- as.numeric(tab$scale)

##Save Blackbear.AIC table for future figures (move to Figures folder in Ch.3_Interactions)
write.csv(tab, "LDscaleanalysis_Blackbear.csv")


op <- par(mar = c(6,6,5,3) + 0.2)
plot(tab$scale, tab$weight, xlim=range(tab$scale), ylim=c(0,1), xlab = "", ylab = "", pch=20, cex = 4, cex.axis = 2, cex.lab = 4)
lines(tab$scale[order(tab$scale)], tab$weight[order(tab$scale)], xlim=range(tab$scale), ylim=c(0,1))
title("Blackbear", line = -4, cex.main = 5)
title(xlab = "Scale (m)", line = 4, cex.lab = 4)
title(ylab = "AIC weight", cex.lab = 4)
```
```{r, warning=FALSE, error=FALSE}

summary(B1500)
```
 Top scales are: 1500 m for Black bear and Lynx, 1750 m for Coyote. Add these to data frames for further analyses
```{r}
## Re-load data frames so they DO NOT have all LD scales attached
Occ <- read.csv("Algar60_speciesOccurrence.csv")
Bears <- read.csv("Algar60_speciesOccurrence_SUMMER.csv")

Occ$LD1500 <- Lines$X1500m[match(Occ$Site, Lines$CamStation)]
Occ$LD1750 <- Lines$X1750m[match(Occ$Site, Lines$CamStation)]

Bears$LD1500 <- Lines$X1500m[match(Bears$Site, Lines$CamStation)]


str(Occ)
str(Bears)

write.csv(Occ, "Algar60_speciesOccurrence.csv")
write.csv(Bears, "Algar60_speciesOccurrence_SUMMER.csv")
```