---
title: "Ch1_Moose_modelDistribution"
author: "Erin Tattersall"
date: "May 8, 2018"
output: word_document
---


Modelling detections rates between November 2015 and April 2018 for moose.  
Deciding on most appropriate distribution for response variable.


Proportion of zeros in data
```{r "setup", include=FALSE, cache=FALSE}
knitr::opts_knit$set(root.dir = 'C:/Users/ETattersall/Desktop/Algar_Cam_Traps/Algar_Camera_Traps/Data') #Setting working directory for all code chunks
```

```{r, message=FALSE, echo=FALSE}

library(glmmTMB)
library(bbmle) #AICtab function
library(ggplot2)
library(lmtest)
library(reshape)
library(dplyr)
```
```{r, echo=FALSE, message=FALSE}
#Load detection data
det <- read.csv("Seismic_nov2015-apr2018.csv")
det$X <- NULL

#Load lowland data
low <- read.csv("newAVIE_lowland8buffersizes.csv")

#Combine data
det$low250 <- low$low250[match(det$Site, low$CamStation)]
det$low500 <- low$low500[match(det$Site, low$CamStation)]
det$low750 <- low$low750[match(det$Site, low$CamStation)]
det$low1000 <- low$low1000[match(det$Site, low$CamStation)]
det$low1250 <- low$low1250[match(det$Site, low$CamStation)]
det$low1500 <- low$low1500[match(det$Site, low$CamStation)]
det$low1750 <- low$low1750[match(det$Site, low$CamStation)]
det$low2000 <- low$low2000[match(det$Site, low$CamStation)]

#Load linedensity data
LineDens <- read.csv("AlgarStationsLD_Lines.csv")

# Combine datasets
det$LD250 <- LineDens$X250m[match(det$Site, LineDens$CamStation)]
det$LD500 <- LineDens$X500m[match(det$Site, LineDens$CamStation)]
det$LD750 <- LineDens$X750m[match(det$Site, LineDens$CamStation)]
det$LD1000 <- LineDens$X1000m[match(det$Site, LineDens$CamStation)]
det$LD1250 <- LineDens$X1250m[match(det$Site, LineDens$CamStation)]
det$LD1500 <- LineDens$X1500m[match(det$Site, LineDens$CamStation)]
det$LD1750 <- LineDens$X1750m[match(det$Site, LineDens$CamStation)]
det$LD2000 <- LineDens$X2000m[match(det$Site, LineDens$CamStation)]


#Load line width and veg height
sp <- read.csv("Spatial_covariates.csv")

det$VegHt <- sp$VegHt[match(det$Site, sp$Site)]
det$LineWidth <- sp$LineWidth[match(det$Site, sp$Site)]
```


```{r, echo=FALSE, results='hide'}

#### Moose models ####
## Lowland measured at 250m, LD measured at 1250m


### Exploring distribution and overdispersion (code from Zuur & Ieno, 2016)
##1. Proportion of 0's in data
table(is.na(det$Moose)) #1800 non-NAs --> no NAs present
table(det$Moose == 0) # 116 non-zero values
```
```{r}
sum(det$Moose==0, na.rm = TRUE)/nrow(det)
```
  94% of the data is zeroes --> very likely zero-inflated.  

### Fitting a basic poisson GLM and checking overdispersion, using global model (doesn't yet include SnowDays)
```{r}
glm1 <- glmmTMB(Moose~ Treatment + LineWidth + LD1250 + VegHt + low250 + ActiveDays, data = det, family = poisson)
# Residuals and overdispersion
E1 <- resid(glm1, type="pearson")
N <- nrow(det)
p <- length(coef(glm1))
sum(E1^2)/(N-p)
```
Dispersion value of  1.03 indicates data is not necessarily overdispersed

Simulating data to check probability of calculated dispersion.
```{r, include=FALSE, echo=FALSE, warning=FALSE}
#function for calculating overdispersion (as above)
MyDispersion <- function(y, mu, N, p){
  e <- (y-mu)/sqrt(mu)
  sum(e^2)/(N-p)
}
muFit <- fitted(glm1) #fitted values from model
Ysim <- matrix(nrow = N, ncol = 10000) #matrix storing simulated responses
DispersionSim <- vector(length = 10000)#vector storing Dispersion value
#Loop running simulation of Poisson distributed data and calculating Dispersion value
for(i in 1:10000){
  Ysim[,i] <- rpois(N,lambda = muFit)
  DispersionSim[i] <- MyDispersion(Ysim[,i], muFit, N, p)
}
```
```{r, echo=FALSE}
#Histogram of dispersion statistics
hist(DispersionSim, breaks = 1000, xlim = c(0,5))# Simulated statistics are mostly on either side of 1 -->unlikely to have overdispersion
```
Histogram indicates that an overdispersion statistic of 1.03 is well within the likely distribution of dispersion statistics for Poisson distributed response variables, suggesting that Moose data is not necessarily overdispersed.  

Comparing the proportion of zeros in data to simulated zeros from model shows that Moose data has more zeroes than would be expected in a Poisson GLM
```{r, echo=FALSE}
## Comparing proportions of 0's in simulated data to that in sampled data
zeros <- vector(length = 10000)
for(i in 1:10000){
  zeros[i] <- sum(Ysim[,i] == 0) / N
}

{plot(table(zeros),
     axes = FALSE,
     xlim = c(0.9,1),
     xlab = "Percentage of zeros",
     ylab = "Frequency")

axis(2)
axis(1, 
     at = c(0.90,0.92,0.94,0.96,0.98,1.0),
     labels = c("90%","92%","94%","96%","98%","100%"))
points(x = sum(det$Moose==0, na.rm = TRUE)/ N,
       y = 0, pch = 16, cex = 5, col = 2)}
```
  This presents a case for using zero-inflated models, which can be verified with model selection of GLMMs
## Model selection: choosing model form and distribution  

Comparing the same GLMM (including random effects of Site and Month) modeled as a poisson, nb, ZIP and ZINB (with nbinom1 and nbinom2 differing in how variance changes with mean) yields:
```{r, message=FALSE}
## Model comparisons of distributions and zero-inflation
glm1 <- glmmTMB(Moose~ Treatment + LineWidth + LD1250 + VegHt + low250 + Dist2Water_km + ActiveDays + (1| Site) + (1|Month), data = det, family = poisson)
glm2 <- glmmTMB(Moose~ Treatment + LineWidth + LD1250 + VegHt + low250 + Dist2Water_km + ActiveDays + (1| Site) + (1|Month), data = det, family = nbinom1(link= "log"))
glm3 <- glmmTMB(Moose~ Treatment + LineWidth + LD1250 + VegHt + low250 + Dist2Water_km + ActiveDays + (1| Site) + (1|Month), data = det, family = nbinom2(link = "log"))
glm4 <- glmmTMB(Moose~ Treatment + LineWidth + LD1250 + VegHt + low250 + Dist2Water_km + ActiveDays + (1| Site) + (1|Month), zi = ~1, data = det, family = poisson)
glm5 <- glmmTMB(Moose~ Treatment + LineWidth + LD1250 + VegHt + low250 + Dist2Water_km + ActiveDays +(1| Site) + (1|Month), zi = ~1, data = det, family = nbinom1(link= "log")) ## warning 'matrix not positive definite'
glm6 <- glmmTMB(Moose~ Treatment + LineWidth + LD1250 + VegHt + low250 + Dist2Water_km + ActiveDays + (1| Site) + (1|Month), zi = ~1, data = det, family = nbinom2(link= "log"))
```
```{r, echo=FALSE}
modnames <- c("Poisson", "Nbinom1", "Nbinom2", "ZIP", "ZINB1", "ZINB2")
ICtab(glm1,glm2,glm3,glm4,glm5,glm6, mnames = modnames, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)

```
ZINB1 displayed a warning when modeled, but parameter estimates + s.e. obtained, so included in model selection.  
 Nbinom2 model's summary output is:
```{r, echo = FALSE}
summary(glm3)
```
 ZINB model output:
```{r, echo = FALSE}
summary(glm6)
```
 Active Days affects the probability of observing a zero in data --> should be included in ZI model. It could be argued that it should NOT be included in conditional. I will test both  
```{r, warning=FALSE}
glm7 <- glmmTMB(Moose~ Treatment + LineWidth + LD1250 + VegHt + low250 + Dist2Water_km + ActiveDays +(1| Site) + (1|Month), zi = ~ActiveDays, data = det, family = nbinom2(link= "log"))
glm8 <- glmmTMB(Moose~ Treatment + LineWidth + LD1250 + VegHt + low250 + Dist2Water_km +(1| Site) + (1|Month), zi = ~ActiveDays, data = det, family = nbinom2(link= "log"))
summary(glm8)
```
```{r, echo=FALSE}
modnames <- c("Poisson", "Nbinom1", "Nbinom2", "ZIP", "ZINB1", "ZINB2","ZINB2-AD2","ZINB2-AD1")
ICtab(glm1,glm2,glm3,glm4,glm5,glm6, glm7, glm8, mnames = modnames, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
```
 Nbinom2 without zero-inflation still comes out as top model. However, there is evidence that Moose detection data is zero-inflated, justifying including zero-inflation a priori. Further, examining the output for ZINB2-AD1 shows that ActiveDays in the ZI model has a small but near significant effect on detecting structured zeros (and that there is a high chance of observing a structured zero in data regardless).  
 I will therefore model moose data as zero-inflated nbinom2 with ActiveDays in the ZI model. 
 
 
 # Model hypotheses  
 ## Finding random structure
```{r, echo=FALSE}
r0 <- glmmTMB(Moose~ LineWidth + LD1250 + VegHt + Dist2Water_km + low250*Treatment, data = det, zi=~ActiveDays,family = nbinom2)
rSite <- glmmTMB(Moose~ LineWidth + LD1250 + VegHt + low250*Treatment + Dist2Water_km +  (1|Site), data = det,zi=~ActiveDays, family = nbinom2) 
rMonth <- glmmTMB(Moose~ LineWidth + LD1250 + VegHt + low250*Treatment + Dist2Water_km + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)
r2 <- glmmTMB(Moose~ LineWidth + LD1250 + VegHt + low250*Treatment + Dist2Water_km + (1|Site) + (1|Month), data = det, zi=~ActiveDays, family = nbinom2)
ICtab(r0, rSite, rMonth, r2, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
```
Continue modelling with 2 random effects
 