---
title: "Ch1_models_caribou"
author: "Erin Tattersall"
date: "April 27, 2018"
output: html_document
---

  Based on model selection comparison of underlying distributions and zero-inflation, I chose an nbinom1 distribution for caribou data (see Ch1_caribou_modelDistribution.Rmd)    
Here I will:  
1. Select random effects to model random structure  
2. Build models with environmental covariates only  
3. Build hypothesis models with line covariates + environmental  
4. Perform model selection with AIC  
5. Calculate evidence ratios (AICwt of Best Model/ AICwt of other models)  
6. Checking residuals of Top Model
7. Model Averaging?
8. Standardize parameter estimates for easy interpretation

```{r, echo=FALSE, message=FALSE}
library(glmmTMB)
library(bbmle) #AICtab function
library(ggplot2)
library(lmtest)
library(reshape)
library(dplyr)
library(AICcmodavg)

setwd("C:/Users/ETattersall/Desktop/Algar_Cam_Traps/Algar_Camera_Traps/Data")

#Load detection data
det <- read.csv("MonthlyDetections_nov2015-nov2017.csv")
det$X.1 <- NULL
det$X <- NULL

#Load lowland data
low <- read.csv("newAVIE_lowland8buffersizes.csv")

#Combine data
det$low250 <- low$low250[match(det$Site, low$CamStation)]
det$low500 <- low$low500[match(det$Site, low$CamStation)]
det$low750 <- low$low750[match(det$Site, low$CamStation)]
det$low1000 <- low$low1000[match(det$Site, low$CamStation)]
det$low1250 <- low$low1250[match(det$Site, low$CamStation)]
det$low1500 <- low$low1500[match(det$Site, low$CamStation)]
det$low1750 <- low$low1750[match(det$Site, low$CamStation)]
det$low2000 <- low$low2000[match(det$Site, low$CamStation)]

#Load linedensity data
LineDens <- read.csv("AlgarStationsLD_Lines.csv")

# Combine datasets
det$LD250 <- LineDens$X250m[match(det$Site, LineDens$CamStation)]
det$LD500 <- LineDens$X500m[match(det$Site, LineDens$CamStation)]
det$LD750 <- LineDens$X750m[match(det$Site, LineDens$CamStation)]
det$LD1000 <- LineDens$X1000m[match(det$Site, LineDens$CamStation)]
det$LD1250 <- LineDens$X1250m[match(det$Site, LineDens$CamStation)]
det$LD1500 <- LineDens$X1500m[match(det$Site, LineDens$CamStation)]
det$LD1750 <- LineDens$X1750m[match(det$Site, LineDens$CamStation)]
det$LD2000 <- LineDens$X2000m[match(det$Site, LineDens$CamStation)]


#Load line width and veg height
sp <- read.csv("Spatial_covariates.csv")

det$VegHt <- sp$VegHt[match(det$Site, sp$Site)]
det$LineWidth <- sp$LineWidth[match(det$Site, sp$Site)]




## Visualising patterns using predict function (predicting new data, given the best-fit model)
## Need to first remove NAs from explanatory variables
newdat <-  det[ , c(1,2,12:34)] #Naming columns in df
newdat <- na.omit(newdat) ## Exluding NA rows, which causes lengths to differ
```

## Finding random structure
```{r, echo=FALSE}
r0 <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays, data = det, family = nbinom1)
rSite <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays + (1|Site), data = det, family = nbinom1) 
rMonth <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays + (1|Month), data = det, family = nbinom1)
r2 <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)
ICtab(r0, rSite, rMonth, r2, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
```
Continue modelling with 2 random effects  

## Environmental models  
Model Name  | Covariates
----------- | -------------------
E1          | None
E2          | low1750 + SnowDays
E3          | low1750
E4          | SnowDays

```{r, echo=FALSE}
E1 <- glmmTMB(Caribou~1 + (1|Site) + (1|Month), data = det, family = nbinom1)

#2. Global model
E2 <- glmmTMB(Caribou~low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#3. Lowland only
E3 <- glmmTMB(Caribou~low1750 + (1|Site) + (1|Month), data = det, family = nbinom1)

#4. Snow only
E4 <- glmmTMB(Caribou~SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

ICtab(E1, E2, E3, E4, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE) 
```
Continue modelling Line characteristics with both environmental variables  

## Line characteristics  
Model Name  | Covariates
----------- | -------------------
L1          | Treatment + low1750 + SnowDays
L2          | VegHt + low1750 + SnowDays
L3          | LD1750 + low1750 + SnowDays
L4          | LineWidth + low1750 + SnowDays
L5          | Treatment + LineWidth + low1750 + SnowDays
L6          | LineWidth + VegHt + low1750 + SnowDays
L7          | Treatment + LD1750 + low1750 + SnowDays
L8          | LD1750 + VegHt + low1750 + SnowDays
L9          | Treatment + VegHt + low1750 + SnowDays
L10         | Treatment + LineWidth + VegHt + low1750 + SnowDays
L11         | Treatment + LineWidth + LD1750 + low1750 + SnowDays
L12         | Treatment + VegHt + LD1750 + low1750 + SnowDays
L13         | LineWidth + VegHt + LD1750 + low1750 + SnowDays
L14         | Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays  

```{r, echo = FALSE, warning=FALSE, message=FALSE}
#1. Treatment
L1 <- glmmTMB(Caribou~Treatment + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#2. VegHt
L2 <- glmmTMB(Caribou~ VegHt + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#3. Line density
L3 <- glmmTMB(Caribou~ LD1750 + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#4. Line Width
L4 <- glmmTMB(Caribou~ LineWidth + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#5. Treatment + LineWidth
L5 <- glmmTMB(Caribou~ Treatment + LineWidth + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#6. LineWidth + VegHt
L6 <- glmmTMB(Caribou~ LineWidth + VegHt + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#7. Treatment + Line density
L7 <- glmmTMB(Caribou~ Treatment + LD1750 + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#8. Line density and VegHt
L8 <- glmmTMB(Caribou~ LD1750 + VegHt + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#9. VegHt + Treatment
L9 <- glmmTMB(Caribou~ Treatment + VegHt + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#10. Treatment, LineWidth, VegHt
L10 <- glmmTMB(Caribou~ Treatment + LineWidth + VegHt + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#11. Treatment, LineWidth, Line density
L11 <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#12. Treatment, Line density, VegHt
L12 <- glmmTMB(Caribou~ Treatment + VegHt + LD1750 + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#13. LineWidth, VegHt, Line density
L12 <- glmmTMB(Caribou~ LineWidth + VegHt + LD1750 + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

#14. Global model - Treatment, Line density, VegHt, LineWidth
L14 <-  glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)

CaribouAIC <- ICtab(E1, E2, E3, E4, L1, L2, L3, L4, L5, L6, L7, L8, L9, L10, L11, L12, L13, L14, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
CaribouAIC
```
  Seven models within 2 dAIC points of each other, with model weights between 8-17%  
  This suggests that all variables are somewhat influential on the response variable, but to varying degrees  
  
  Calculating evidence ratios (AIC wt of best model/AIC weight of others) gives:
  
```{r,echo=FALSE, results='hide'}
EvR <- function(AICwt.high, AICwt.low){
  EvR <- AICwt.high/AICwt.low
  print(EvR)
}
EvR(CaribouAIC$weight[1], CaribouAIC$weight[2])
CaribouWt <- CaribouAIC$weight
CaribouER <- vector(length=17)
for(i in 2:18){
  CaribouER[i-1] <- EvR(CaribouWt[1], CaribouWt[i])
}
```
```{r,echo=FALSE}
CaribouER <- append("", CaribouER)
ER <- as.data.frame(CaribouER)
ER$dLogLikelihood <- CaribouAIC$dLogLik
ER$dAIC <- CaribouAIC$dAIC
ER$Modelweight <- CaribouAIC$weight
ER$ModelNames <- c("L9", "L5", "L2", "L8", "L11", "L10", "L14", "L4", "L12", "L6","L13", "L7", "L1", "L3", "E2", "E3", "E4", "E1")

ER <- ER %>% select(ModelNames, dLogLikelihood, dAIC, Modelweight, CaribouER)
colnames(ER) <- c("ModelNames", "dLogLikelihood", "dAIC", "Modelweight", "EvidenceRatio")
ER

```
  
````{r, echo=FALSE}
summary(L9)
```

## Checking Residuals of Top model

### Calculating Overdispersion statistic:
```{r, echo=FALSE}
dispfun <- function(m) {
  r <- residuals(m,type="pearson")
  n <- df.residual(m)
  dsq <- sum(r^2)
  c(dsq=dsq,n=n,disp=dsq/n)
}
dispfun(L9)
```
  According to a nbinom1 distribution, the response variable is not overdispersed

### Plotting residuals against fitted values and predicted values for all covariates
```{r, echo=FALSE}

E1 <- resid(L9, type = "pearson") #Pearson residuals
F1 <- fitted(L9)
op <- par(mfrow = c(3,3), mar = c(5,4,1,2))
plot(x = F1,
     y = E1,
     xlab = "Fitted values",
     ylab = "Pearson residuals")
abline(h=0, lty=2)
hist(E1, xlab = "Residuals", main = "")
## Need to use newdat for covariates to remove NAs
plot(newdat$Treatment, E1, xlab = "Treatment", ylab = "Residuals")
plot(newdat$LineWidth, E1, xlab = "Line Width", ylab = "Residuals")
plot(newdat$low1750, E1, xlab = "Proportion of Lowland habitat", ylab = "Residuals")
plot(newdat$SnowDays, E1, xlab = "Snow Days per Month", ylab = "Residuals")
plot(newdat$Site, E1, xlab = "Site", ylab = "Residuals")
plot(newdat$Month, E1, xlab = "Month", ylab = "Residuals")
par(op)


```
