---
title: "Ch1_Blackbear_modelDistribution"
author: "Erin Tattersall"
date: "May 8, 2018"
output: word_document
---

Modelling detections rates between November 2015 and April 2018 for black bear.  
Deciding on most appropriate distribution for response variable.


Proportion of zeros in data
```{r "setup", include=FALSE, cache=FALSE}
knitr::opts_knit$set(root.dir = 'C:/Users/ETattersall/Desktop/Algar_Cam_Traps/Algar_Camera_Traps/Data') #Setting working directory for all code chunks
```

```{r, message=FALSE, echo=FALSE}

library(glmmTMB)
library(bbmle) #AICtab function
library(ggplot2)
library(lmtest)
library(reshape)
library(dplyr)
```
```{r, echo=FALSE, message=FALSE}
#Load detection data
getwd()
det <- read.csv("Seismic_nov2015-apr2018.csv")
det$X <- NULL

# Select for bear's Active seasons only - April - October, 2016 and 2017
det <- det %>% filter(Yr_Month == "2016-04" | Yr_Month == "2016-05" | Yr_Month == "2016-06"| Yr_Month == "2016-07"| Yr_Month == "2016-08"| Yr_Month == "2016-09"| Yr_Month == "2016-10"| Yr_Month == "2017-04" | Yr_Month == "2017-05" | Yr_Month == "2017-06"| Yr_Month == "2017-07"| Yr_Month == "2017-08"| Yr_Month == "2017-09"| Yr_Month == "2017-10") %>% select(Site, Treatment,Yr_Month, Site_ym, Blackbear, Month, ActiveDays)

#Load lowland data
low <- read.csv("newAVIE_lowland8buffersizes.csv")

#Combine data
det$low250 <- low$low250[match(det$Site, low$CamStation)]
det$low500 <- low$low500[match(det$Site, low$CamStation)]
det$low750 <- low$low750[match(det$Site, low$CamStation)]
det$low1000 <- low$low1000[match(det$Site, low$CamStation)]
det$low1250 <- low$low1250[match(det$Site, low$CamStation)]
det$low1500 <- low$low1500[match(det$Site, low$CamStation)]
det$low1750 <- low$low1750[match(det$Site, low$CamStation)]
det$low2000 <- low$low2000[match(det$Site, low$CamStation)]

#Load linedensity data
LineDens <- read.csv("AlgarStationsLD_Lines.csv")

# Combine datasets
det$LD250 <- LineDens$X250m[match(det$Site, LineDens$CamStation)]
det$LD500 <- LineDens$X500m[match(det$Site, LineDens$CamStation)]
det$LD750 <- LineDens$X750m[match(det$Site, LineDens$CamStation)]
det$LD1000 <- LineDens$X1000m[match(det$Site, LineDens$CamStation)]
det$LD1250 <- LineDens$X1250m[match(det$Site, LineDens$CamStation)]
det$LD1500 <- LineDens$X1500m[match(det$Site, LineDens$CamStation)]
det$LD1750 <- LineDens$X1750m[match(det$Site, LineDens$CamStation)]
det$LD2000 <- LineDens$X2000m[match(det$Site, LineDens$CamStation)]


#Load line width and veg height
sp <- read.csv("Spatial_covariates.csv")

det$VegHt <- sp$VegHt[match(det$Site, sp$Site)]
det$LineWidth <- sp$LineWidth[match(det$Site, sp$Site)]
```


```{r, echo=FALSE, results='hide'}

#### Blackbear models ####
## Lowland measured at 500m, LD measured at 750m


### Exploring distribution and overdispersion (code from Zuur & Ieno, 2016)
##1. Proportion of 0's in data
table(is.na(det$Blackbear)) #840 non-NAs --> no NAs present
table(det$Blackbear == 0) # 147 non-zero values
```
```{r}
sum(det$Blackbear==0, na.rm = TRUE)/nrow(det)
```
  82.5% of the data is zeroes --> likely zero-inflated.  

### Fitting a basic poisson GLM and checking overdispersion, using global model (doesn't yet include SnowDays)
```{r}
glm1 <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + ActiveDays, data = det, family = poisson)
# Residuals and overdispersion
E1 <- resid(glm1, type="pearson")
N <- nrow(det)
p <- length(coef(glm1))
sum(E1^2)/(N-p)
```
Dispersion value of  1.88 indicates data is probably overdispersed

Simulating data to check probability of calculated dispersion.
```{r, include=FALSE, echo=FALSE, warning=FALSE}
#function for calculating overdispersion (as above)
MyDispersion <- function(y, mu, N, p){
  e <- (y-mu)/sqrt(mu)
  sum(e^2)/(N-p)
}
muFit <- fitted(glm1) #fitted values from model
Ysim <- matrix(nrow = N, ncol = 10000) #matrix storing simulated responses
DispersionSim <- vector(length = 10000)#vector storing Dispersion value
#Loop running simulation of Poisson distributed data and calculating Dispersion value
for(i in 1:10000){
  Ysim[,i] <- rpois(N,lambda = muFit)
  DispersionSim[i] <- MyDispersion(Ysim[,i], muFit, N, p)
}
```
```{r, echo=FALSE}
#Histogram of dispersion statistics
hist(DispersionSim, breaks = 1000, xlim = c(0,3))# Simulated statistics are mostly on either side of 1 -->unlikely to have overdispersion
```
Histogram indicates that an overdispersion statistic of 1.88 is toward the high edge of the likely distribution of dispersion statistics for Poisson distributed response variables, suggesting that Blackbear data is probably overdispersed.  

Comparing the proportion of zeros in data to simulated zeros from model shows that Blackbear data has more zeroes than would be expected in a Poisson GLM
```{r, echo=FALSE}
## Comparing proportions of 0's in simulated data to that in sampled data
zeros <- vector(length = 10000)
for(i in 1:10000){
  zeros[i] <- sum(Ysim[,i] == 0) / N
}

{plot(table(zeros),
     axes = FALSE,
     xlim = c(0.65,0.9),
     xlab = "Percentage of zeros",
     ylab = "Frequency")

axis(2)
axis(1, 
     at = c(0.65,0.7, 0.75, 0.8, 0.85),
     labels = c("65%","70%","75%","80%","85%"))
points(x = sum(det$Blackbear==0, na.rm = TRUE)/ N,
       y = 0, pch = 16, cex = 5, col = 2)}
```
  This presents a case for using zero-inflated models, which can be verified with model selection of GLMMs
## Model selection: choosing model form and distribution  

Comparing the same GLMM (including random effects of Site and Month) modeled as a poisson, nb, ZIP and ZINB (with nbinom1 and nbinom2 differing in how variance changes with mean) yields:
```{r, message=FALSE}
## Model comparisons of distributions and zero-inflation
glm1 <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + ActiveDays + (1| Site) + (1|Month), data = det, family = poisson)
glm2 <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + ActiveDays + (1| Site) + (1|Month), data = det, family = nbinom1(link= "log")) #warning matrix not positive definite
glm3 <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + ActiveDays + (1| Site) + (1|Month), data = det, family = nbinom2(link = "log"))
glm4 <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + ActiveDays + (1| Site) + (1|Month), zi = ~1, data = det, family = poisson)
glm5 <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + ActiveDays +(1| Site) + (1|Month), zi = ~1, data = det, family = nbinom1(link= "log")) ## warning 'matrix not positive definite' and 'lgamma value out of range'
glm6 <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + ActiveDays + (1| Site) + (1|Month), zi = ~1, data = det, family = nbinom2(link= "log")) ## warning 'matrix not positive definite'
```
```{r, echo=FALSE}
modnames <- c("Poisson", "Nbinom1", "Nbinom2", "ZIP", "ZINB1", "ZINB2")
ICtab(glm1,glm2,glm3,glm4,glm5,glm6, mnames = modnames, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)

```
Nbinom1, ZINB1, and ZINB2 displayed a warning when modeled, but parameter estimates + s.e. obtained, so included in model selection.  
 Nbinom2 model's summary output is:
```{r, echo = FALSE}
summary(glm3)
```
 ZINB model output:
```{r, echo = FALSE}
summary(glm6)
```
 Top model Nbinom2 did not result in any warnings, but both ZINB models did. Proceed with ZINB with caution.  
 Active Days affects the probability of observing a zero in data --> should be included in ZI model. It could be argued that it should NOT be included in conditional. I will test both  
```{r, warning=FALSE}
glm7 <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + ActiveDays +(1| Site) + (1|Month), zi = ~ActiveDays, data = det, family = nbinom2(link= "log"))
glm8 <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + (1| Site) + (1|Month), zi = ~ActiveDays, data = det, family = nbinom2(link= "log"))
summary(glm8)
```
```{r, echo=FALSE}
modnames <- c("Poisson", "Nbinom1", "Nbinom2", "ZIP", "ZINB1", "ZINB2","ZINB2-AD2","ZINB2-AD1")
ICtab(glm1,glm2,glm3,glm4,glm5,glm6, glm7, glm8, mnames = modnames, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
```
  Adding ActiveDays to ZI model resulted in a model without convergence issues that had top model weight
 I will therefore model Blackbear data as zero-inflated nbinom2 with ActiveDays in the ZI model. 
 
 
 # Model hypotheses  
 ## Finding random structure
```{r}
r0 <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500, zi = ~ActiveDays, data = det, family = nbinom2(link= "log"))
rSite <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + (1| Site), zi = ~ActiveDays, data = det, family = nbinom2(link= "log")) 
rMonth <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + (1|Month), zi = ~ActiveDays, data = det, family = nbinom2(link= "log"))
r2 <- glmmTMB(Blackbear~ Treatment + LineWidth + LD750 + VegHt + low500 + (1| Site) + (1|Month), zi = ~ActiveDays, data = det, family = nbinom2(link= "log"))
ICtab(r0, rSite, rMonth, r2, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
```
 Models testing random structure resulted in convergence issues, despite having worked with similar structure previously. I will continue modelling with 2 random effects for consistency and because it makes sense (justification stated elsewhere)
