---
title: "Ch1_models_Caribou"
author: "Erin Tattersall"
date: "April 26, 2018"
output: word_document
---

Modelling detections rates between November 2015 and November 2017 for caribou, wolves, black bears, white-tailed deer, and moose.
Seismic line characteristic covariates: treatment, vegetation height, line connectivity, line width
Environmental covariates: proportion of lowland habitat, SnowDays, Distance to water

For full script, see Ch1_models.R

1. Caribou

a. Checked for data for 0's and overdispersion

Proportion of zeros in data
```{r, echo=FALSE, message=FALSE}
library(glmmTMB)
library(bbmle) #AICtab function
library(ggplot2)
library(lmtest)
library(reshape)
library(dplyr)

setwd("C:/Users/ETattersall/Desktop/Algar_Cam_Traps/Algar_Camera_Traps/Data")

#Load detection data
det <- read.csv("MonthlyDetections_nov2015-nov2017.csv")
det$X.1 <- NULL
det$X <- NULL

#Load lowland data
low <- read.csv("newAVIE_lowland8buffersizes.csv")

#Combine data
det$low250 <- low$low250[match(det$Site, low$CamStation)]
det$low500 <- low$low500[match(det$Site, low$CamStation)]
det$low750 <- low$low750[match(det$Site, low$CamStation)]
det$low1000 <- low$low1000[match(det$Site, low$CamStation)]
det$low1250 <- low$low1250[match(det$Site, low$CamStation)]
det$low1500 <- low$low1500[match(det$Site, low$CamStation)]
det$low1750 <- low$low1750[match(det$Site, low$CamStation)]
det$low2000 <- low$low2000[match(det$Site, low$CamStation)]

#Load linedensity data
LineDens <- read.csv("AlgarStationsLD_Lines.csv")

# Combine datasets
det$LD250 <- LineDens$X250m[match(det$Site, LineDens$CamStation)]
det$LD500 <- LineDens$X500m[match(det$Site, LineDens$CamStation)]
det$LD750 <- LineDens$X750m[match(det$Site, LineDens$CamStation)]
det$LD1000 <- LineDens$X1000m[match(det$Site, LineDens$CamStation)]
det$LD1250 <- LineDens$X1250m[match(det$Site, LineDens$CamStation)]
det$LD1500 <- LineDens$X1500m[match(det$Site, LineDens$CamStation)]
det$LD1750 <- LineDens$X1750m[match(det$Site, LineDens$CamStation)]
det$LD2000 <- LineDens$X2000m[match(det$Site, LineDens$CamStation)]


#Load line width and veg height
sp <- read.csv("Spatial_covariates.csv")

det$VegHt <- sp$VegHt[match(det$Site, sp$Site)]
det$LineWidth <- sp$LineWidth[match(det$Site, sp$Site)]




## Visualising patterns using predict function (predicting new data, given the best-fit model)
## Need to first remove NAs from explanatory variables
newdat <-  det[ , c(1,2,12:34)] #Naming columns in df
newdat <- na.omit(newdat) ## Exluding NA rows, which causes lengths to differ

#### Caribou models ####
## Lowland measured at 1750m, LD measured at 1750m
# Not including Dist2Water --> no corresponding hypothesis

### Exploring distribution and overdispersion (code from Zuur & Ieno, 2016)
##1. Proportion of 0's in data
table(is.na(det$Caribou)) #647 NAs, 853 non-NAs
table(det$Caribou == 0)
```
```{r}
sum(det$Caribou==0, na.rm = TRUE)/nrow(det)

```
Fitting a basic poisson GLM and checking overdispersion, using global model
```{r}
glm1 <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays, data = det, family = poisson)
# Residuals and overdispersion
E1 <- resid(glm1, type="pearson")
N <- nrow(det)
p <- length(coef(glm1))
sum(E1^2)/(N-p)
```
Simulating data to check probability of calculated dispersion.
```{r, include=FALSE, echo=FALSE, warning=FALSE}
#function for calculating overdispersion (as above)
MyDispersion <- function(y, mu, N, p){
  e <- (y-mu)/sqrt(mu)
  sum(e^2)/(N-p)
}
muFit <- fitted(glm1) #fitted values from model
Ysim <- matrix(nrow = N, ncol = 100000) #matrix storing simulated responses
DispersionSim <- vector(length = 100000)#vector storing Dispersion value
#Loop running simulation of Poisson distributed data and calculating Dispersion value
for(i in 1:100000){
  Ysim[,i] <- rpois(N,lambda = muFit)
  DispersionSim[i] <- MyDispersion(Ysim[,i], muFit, N, p) #warnings generated but vector obtained
}
```
```{r, echo=FALSE}
#Histogram of dispersion statistics
hist(DispersionSim)# Simulated statistics are mostly on either side of 1 -->unlikely to have overdispersion
```
Histogram indicates that an overdispersion statistic of 0.815 is well within the likely distribution, indicating that the data is not overdispersed.

Comparing the proportion of zeros in data to simulated data for model actually shows that Caribou data has far fewer zeros than would be expected in a Poisson distribution GLM. This may simply mean that a Poisson GLM is not appropriate for this data.
```{r, echo=FALSE}
## Comparing proportions of 0's in simulated data to that in sampled data
zeros <- vector(length = 100000)
for(i in 1:100000){
  zeros[i] <- sum(Ysim[,i] == 0) / N
}

plot(table(zeros),
     axes = FALSE,
     xlim = c(0.4, 1),
     xlab = "Percentage of zeros",
     ylab = "Frequency")

axis(2)
axis(1, 
     at = c(0.4, 0.5, 0.6, 0.7, 0.8, 0.9),
     labels = c("40%", "50%", "60%", "70%", "80%", "90%"))
points(x = sum(det$Caribou==0, na.rm = TRUE)/ N,
       y = 0, pch = 16, cex = 5, col = 2)
```

Previously I had decided on using a zero-inflated model a priori to account for the structured nature of zero counts. However, this may misrepresent the data in some cases.

Comparing the same GLMM (including random effects of Site and Month) modeled as a poisson, nb, ZIP and ZINB (with nbinom1 and nbinom2 differing in how variance changes with mean) yields:
```{r}
## Model comparisons of distributions and zero-inflation
glm1 <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays + (1| Site) + (1|Month), data = det, family = poisson)
glm2 <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays + (1| Site) + (1|Month), data = det, family = nbinom1(link= "log"))
glm3 <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays + (1| Site) + (1|Month), data = det, family = nbinom2(link = "log"))
glm4 <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays + (1| Site) + (1|Month), zi = ~1, data = det, family = poisson)
glm5 <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays +(1| Site) + (1|Month), zi = ~1, data = det, family = nbinom1(link= "log"))
glm6 <- glmmTMB(Caribou~ Treatment + LineWidth + LD1750 + VegHt + low1750 + SnowDays + (1| Site) + (1|Month), zi = ~1, data = det, family = nbinom2(link= "log"))
```
```{r, echo=FALSE}
modnames <- c("Poisson", "Nbinom1", "Nbinom2", "ZIP", "ZINB1", "ZINB2")
ICtab(glm1,glm2,glm3,glm4,glm5,glm6, mnames = modnames, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)

```
Where the Nbinom1 model's summary output is:
```{r, echo = FALSE}
summary(glm2)
```
 For caribou models, I will therefore use non-zero inflated GLMMs with a nbinom1 distribution (where variance changes linearly with the mean).  
 # Model hypotheses  
 ## Finding random structure
```{r, echo=FALSE}
r0 <- glmmTMB(Caribou~ LineWidth + LD1750 + VegHt + low1750*Treatment + SnowDays, data = det, family = nbinom1)
rSite <- glmmTMB(Caribou~ LineWidth + LD1750 + VegHt + low1750*Treatment + SnowDays + (1|Site), data = det, family = nbinom1) 
rMonth <- glmmTMB(Caribou~ LineWidth + LD1750 + VegHt + low1750*Treatment + SnowDays + (1|Month), data = det, family = nbinom1)
r2 <- glmmTMB(Caribou~ LineWidth + LD1750 + VegHt + low1750*Treatment + SnowDays + (1|Site) + (1|Month), data = det, family = nbinom1)
ICtab(r0, rSite, rMonth, r2, type= "AIC", weights = TRUE, delta = TRUE, logLik = TRUE, sort=TRUE)
```
Continue modelling with 2 random effects
 